---
title: "Region-Specific Emission Targets"
output: html_document
date: "How to define region-specific emission targets, either as year-based targets or emission budgets:"
---


<style type="text/css">

   .main-container {max-width: 90%;}
   .row {display: flex;}
   .column {}
   .column66 {width: 66%}
   .column60 {width: 60%}
   .column40 {width: 40%}
   .column33 {width: 33%}
   .divisor {width: 2.5%}
   
   body{
  font-family: Helvetica;
  font-size: 1.2em;
}
/* Headers */
h1,h2,h3,h4,h5,h6{
  font-size: 1.5em;
} 

</style>


<div class = "row">

<div class = "column66">

<div class = "row">

<div class = "column40">


### Setting Emission Targets: `cm_emiMktTarget`

- require `regipol` to be set to `regiCarbonPrice`


### Options  
| **Option**                                              | **Description**                                                       |
|---------------------------------------------------------|-----------------------------------------------------------------------|
| `off`                                                   | No regional emission target                                           |
| `scenario_tag`                                          | Targets defined in module 47 declarations under the scenario tag      |
| `2020.2050.EU27_regi.all.budget.netGHG_noBunkers 72`    | Explicitly defined target configuration                               |
|                                                         |                                                                       |


### CO2 Tax Curve Shape  

| **Segment**           | **Description**                                                                                         |
|-----------------------|---------------------------------------------------------------------------------------------------------|
| Pre-target years      | Linear increase from the starting year (`initial_year`) to the target year (`target_year`)              |
| Post-target years     | Annual increase based on the `cm_postTargetIncrease` value (in EUR per tCO2)                            |
|                                                         |                                                                       |


</div>

<div class = "divisor">

</div>

<div class = "column60">

### EU-27 target example (Germany and EU-27)

A.  fixed historical value 
A.  EU-27 57% reduction: `2020.2030.EU27_regi.all.year.netGHG_LULUCFGrassi_intraRegBunker 2.191`<br>and DEU 65% reduction: `2020.2030.DEU.all.year.netGHG_noLULUCF_noBunkers 0.42`
A.  effect of DEU 2045 net-neutral target on EU-27 aggregated price: `2035.2045.DEU.all.year.netGHG_LULUCFGrassi 0.0001`
A.  EU-27 net-neutral 2050 target: `2020.2050.EU27.all.year.netGHG_LULUCFGrassi 0.0001`


```{r data, echo=FALSE, include=FALSE}

library(dplyr)

co2price <- data.frame(period=c(18262, 20089, 21915, 23741, 25567, 27394, 29220, 31046, 32872),value=c(31.854417192, 86.792451525, 141.656675121, 213.747136551, 284.199401304, 355.893275439, 401.936467725, 402.420083247, 402.423863166)) %>% mutate(period = as.Date(period,origin="1970-01-01"))

ETSprice <- data.frame(period=c(19878, 19877, 19874, 19873, 19872, 19871, 19870, 19867, 19866, 19865, 19864, 19863, 19860, 19859, 19858, 19857, 19856, 19853, 19852, 19851, 19850, 19849, 19846, 19845, 19844, 19843, 19842, 19839, 19838, 19837, 19836, 19835, 19832, 19831, 19830, 19829, 19828, 19825, 19824, 19823, 19822, 19821, 19818, 19817, 19816, 19815, 19810, 19809, 19808, 19807, 19804, 19803, 19802, 19801, 19800, 19797, 19796, 19795, 19794, 19793, 19790, 19789, 19788, 19787, 19786, 19783, 19782, 19781, 19780, 19779, 19776, 19775, 
    19774, 19773, 19772, 19769, 19768, 19767, 19766, 19765, 19762, 19761, 19760, 19759, 19758, 19755, 19754, 19753, 19752, 19751, 19748, 19747, 19746, 19745, 19744, 19741, 19740, 19739, 19738, 19737, 19734, 19733, 19732, 19731, 19730, 19727, 19726, 19725, 19724, 19720, 19719, 19718, 19713, 19712, 19711, 19710, 19709, 19706, 19705, 19704, 19703, 19702, 19699, 19698, 19697, 19696, 19695, 19692, 19691, 19690, 19689, 19688, 19685, 19684, 19683, 19682, 19681, 19678, 19677, 19676, 19675, 19674, 19671, 
    19670, 19669, 19668, 19667, 19664, 19663, 19662, 19661, 19660, 19657, 19656, 19655, 19654, 19653, 19650, 19649, 19648, 19647, 19646, 19643, 19642, 19641, 19640, 19639, 19636, 19635, 19634, 19633, 19632, 19629, 19628, 19627, 19626, 19625, 19622, 19621, 19620, 19619, 19618, 19615, 19614, 19613, 19612, 19611, 19608, 19607, 19606, 19605, 19604, 19601, 19600, 19599, 19598, 19597, 19594, 19593, 19592, 19591, 19590, 19587, 19586, 19585, 19584, 19583, 19580, 19579, 19578, 19577, 19576, 19573, 19572, 
    19571, 19570, 19569, 19566, 19565, 19564, 19563, 19562, 19559, 19558, 19557, 19556, 19555, 19552, 19551, 19550, 19549, 19548, 19545, 19544, 19543, 19542, 19541, 19538, 19537, 19536, 19535, 19534, 19531, 19530, 19529, 19528, 19527, 19524, 19523, 19522, 19521, 19520, 19517, 19516, 19515, 19514, 19513, 19510, 19509, 19508, 19507, 19506, 19503, 19502, 19501, 19500, 19499, 19496, 19495, 19494, 19493, 19492, 19489, 19488, 19487, 19486, 19485, 19482, 19481, 19480, 19479, 19478, 19475, 19474, 19473, 
    19472, 19471, 19468, 19467, 19466, 19465, 19464, 19461, 19460, 19459, 19458, 19453, 19452, 19451, 19450, 19447, 19446, 19445, 19444, 19443, 19440, 19439, 19438, 19437, 19436, 19433, 19432, 19431, 19430, 19429, 19426, 19425, 19424, 19423, 19422, 19419, 19418, 19417, 19416, 19415, 19412, 19411, 19410, 19409, 19408, 19405, 19404, 19403, 19402, 19401, 19398, 19397, 19396, 19395, 19394, 19391, 19390, 19389, 19388, 19387, 19384, 19383, 19382, 19381, 19380, 19377, 19376, 19375, 19374, 19373, 19370, 
    19369, 19368, 19367, 19366, 19363, 19362, 19361, 19360, 19359, 19356, 19355, 19354, 19353, 19349, 19348, 19347, 19346, 19345, 19342, 19341, 19340, 19339, 19338, 19335, 19334, 19333, 19332, 19331, 19328, 19327, 19326, 19325, 19324, 19321, 19320, 19319, 19318, 19317, 19314, 19313, 19312, 19311, 19310, 19307, 19306, 19305, 19304, 19303, 19300, 19299, 19298, 19297, 19296, 19293, 19292, 19291, 19290, 19289, 19286, 19285, 19284, 19283, 19282, 19279, 19278, 19277, 19276, 19275, 19272, 19271, 19270, 
    19269, 19268, 19265, 19264, 19263, 19262, 19261, 19258, 19257, 19256, 19255, 19254, 19251, 19250, 19249, 19248, 19247, 19244, 19243, 19242, 19241, 19240, 19237, 19236, 19235, 19234, 19233, 19230, 19229, 19228, 19227, 19226, 19223, 19222, 19221, 19220, 19219, 19216, 19215, 19214, 19213, 19212, 19209, 19208, 19207, 19206, 19205, 19202, 19201, 19200, 19199, 19198, 19195, 19194, 19193, 19192, 19191, 19188, 19187, 19186, 19185, 19184, 19181, 19180, 19179, 19178, 19177, 19174, 19173, 19172, 19171, 
    19170, 19167, 19166, 19165, 19164, 19163, 19160, 19159, 19158, 19157, 19156, 19153, 19152, 19151, 19150, 19149, 19146, 19145, 19144, 19143, 19142, 19139, 19138, 19137, 19136, 19135, 19132, 19131, 19130, 19129, 19128, 19125, 19124, 19123, 19122, 19121, 19118, 19117, 19116, 19115, 19114, 19111, 19110, 19109, 19108, 19107, 19104, 19103, 19102, 19101, 19096, 19095, 19094, 19093, 19090, 19089, 19088, 19087, 19086, 19083, 19082, 19081, 19080, 19079, 19076, 19075, 19074, 19073, 19072, 19069, 19068, 
    19067, 19066, 19065, 19062, 19061, 19060, 19059, 19058, 19055, 19054, 19053, 19052, 19051, 19048, 19047, 19046, 19045, 19044, 19041, 19040, 19039, 19038, 19037, 19034, 19033, 19032, 19031, 19030, 19027, 19026, 19025, 19024, 19023, 19020, 19019, 19018, 19017, 19016, 19013, 19012, 19011, 19010, 19009, 19006, 19005, 19004, 19003, 19002, 18999, 18998, 18997, 18996, 18995, 18992, 18991, 18990, 18989, 18988, 18985, 18984, 18983, 18982, 18981, 18978, 18977, 18976, 18975, 18974, 18971, 18970, 18969, 
    18968, 18967, 18964, 18963, 18962, 18961, 18960, 18957, 18956, 18955, 18954, 18953, 18950, 18949, 18948, 18947, 18946, 18943, 18942, 18941, 18940, 18939, 18936, 18935, 18934, 18933, 18932, 18929, 18928, 18927, 18926, 18925, 18922, 18921, 18920, 18919, 18918, 18915, 18914, 18913, 18912, 18911, 18908, 18907, 18906, 18905, 18904, 18901, 18900, 18899, 18898, 18897, 18894, 18893, 18892, 18891, 18890, 18887, 18886, 18885, 18884, 18883, 18880, 18879, 18878, 18877, 18876, 18873, 18872, 18871, 18870, 
    18869, 18866, 18865, 18864, 18863, 18862, 18859, 18858, 18857, 18856, 18855, 18852, 18851, 18850, 18849, 18848, 18845, 18844, 18843, 18842, 18841, 18838, 18837, 18836, 18835, 18834, 18831, 18830, 18829, 18828, 18827, 18824, 18823, 18822, 18821, 18820, 18817, 18816, 18815, 18814, 18813, 18810, 18809, 18808, 18807, 18806, 18803, 18802, 18801, 18800, 18799, 18796, 18795, 18794, 18793, 18792, 18789, 18788, 18787, 18786, 18785, 18782, 18781, 18780, 18779, 18778, 18775, 18774, 18773, 18772, 18771, 
    18768, 18767, 18766, 18765, 18764, 18761, 18760, 18759, 18758, 18757, 18754, 18753, 18752, 18751, 18750, 18747, 18746, 18745, 18744, 18743, 18740, 18739, 18738, 18737, 18736, 18733, 18732, 18731, 18730, 18729, 18726, 18725, 18724, 18723, 18722, 18718, 18717, 18716, 18715, 18712, 18711, 18710, 18709, 18708, 18705, 18704, 18703, 18702, 18701, 18698, 18697, 18696, 18695, 18694, 18691, 18690, 18689, 18688, 18687, 18684, 18683, 18682, 18681, 18680, 18677, 18676, 18675, 18674, 18673, 18670, 18669, 
    18668, 18667, 18666, 18663, 18662, 18661, 18660, 18659, 18656, 18655, 18654, 18653, 18652, 18649, 18648, 18647, 18646, 18645, 18642, 18641, 18640, 18639, 18638, 18635, 18634, 18633, 18632, 18631, 18627, 18626, 18625, 18624, 18620, 18619, 18618, 18617, 18614, 18613, 18612, 18611, 18610, 18607, 18606, 18605, 18604, 18603, 18600, 18599, 18598, 18597, 18596, 18593, 18592, 18591, 18590, 18589, 18586, 18585, 18584, 18583, 18582, 18579, 18578, 18577, 18576, 18575, 18572, 18571, 18570, 18569, 18568, 
    18565, 18564, 18563, 18562, 18561, 18558, 18557, 18556, 18555, 18554, 18551, 18550, 18549, 18548, 18547, 18544, 18543, 18542, 18541, 18540, 18537, 18536, 18535, 18534, 18533, 18530, 18529, 18528, 18527, 18526, 18523, 18522, 18521, 18520, 18519, 18516, 18515, 18514, 18513, 18512, 18509, 18508, 18507, 18506, 18505, 18502, 18501, 18500, 18499, 18498, 18495, 18494, 18493, 18492, 18491, 18488, 18487, 18486, 18485, 18484, 18481, 18480, 18479, 18478, 18477, 18474, 18473, 18472, 18471, 18470, 18467, 
    18466, 18465, 18464, 18463, 18460, 18459, 18458, 18457, 18456, 18453, 18452, 18451, 18450, 18449, 18446, 18445, 18444, 18443, 18442, 18439, 18438, 18437, 18436, 18435, 18432, 18431, 18430, 18429, 18428, 18425, 18424, 18423, 18422, 18421, 18418, 18417, 18416, 18415, 18414, 18411, 18410, 18409, 18408, 18407, 18404, 18403, 18402, 18401, 18400, 18397, 18396, 18395, 18394, 18393, 18390, 18389, 18388, 18387, 18386, 18383, 18382, 18381, 18380, 18379, 18376, 18375, 18374, 18373, 18372, 18369, 18368, 
    18367, 18366, 18361, 18360, 18359, 18358, 18355, 18354, 18353, 18352, 18351, 18348, 18347, 18346, 18345, 18344, 18341, 18340, 18339, 18338, 18337, 18334, 18333, 18332, 18331, 18330, 18327, 18326, 18325, 18324, 18323, 18320, 18319, 18318, 18317, 18316, 18313, 18312, 18311, 18310, 18309, 18306, 18305, 18304, 18303, 18302, 18299, 18298, 18297, 18296, 18295, 18292, 18291, 18290, 18289, 18288, 18285, 18284, 18283, 18282, 18281, 18278, 18277, 18276, 18275, 18274, 18271, 18270, 18269, 18268, 18267, 
    18264, 18263, 18261, 18260, 18257, 18256, 18254, 18253, 18250, 18249, 18248, 18247, 18246, 18243, 18242, 18241, 18240, 18239, 18236, 18235, 18234, 18233, 18232, 18229, 18228, 18227, 18226, 18225, 18222, 18221, 18220, 18219, 18218, 18215, 18214, 18213, 18212, 18211, 18208, 18207, 18206, 18205, 18204, 18201, 18200, 18199, 18198, 18197, 18194, 18193, 18192, 18191, 18190, 18187, 18186, 18185, 18184, 18183, 18180, 18179, 18178, 18177, 18176, 18173, 18172, 18171, 18170, 18169, 18166, 18165, 18164, 
    18163, 18162, 18159, 18158, 18157, 18156, 18155, 18152, 18151, 18150, 18149, 18148, 18145, 18144, 18143, 18142, 18141, 18138, 18137, 18136, 18135, 18134, 18131, 18130, 18129, 18128, 18127, 18124, 18123, 18122, 18121, 18120, 18117, 18116, 18115, 18114, 18113, 18110, 18109, 18108, 18107, 18106, 18103, 18102, 18101, 18100, 18099, 18096, 18095, 18094, 18093, 18092, 18089, 18088, 18087, 18086, 18085, 18082, 18081, 18080, 18079, 18078, 18075, 18074, 18073, 18072, 18071, 18068, 18067, 18066, 18065, 
    18064, 18061, 18060, 18059, 18058, 18057, 18054, 18053, 18052, 18051, 18050, 18047, 18046, 18045, 18044, 18043, 18040, 18039, 18038, 18037, 18036, 18033, 18032, 18031, 18030, 18029, 18026, 18025, 18024, 18023, 18022, 18019, 18018, 18017, 18016, 18015, 18012, 18011, 18010, 18009, 18004, 18003, 18002, 18001, 17998, 17997, 17996, 17995, 17994, 17991, 17990, 17989, 17988, 17987, 17984, 17983, 17982, 17981, 17980, 17977, 17976, 17975, 17974, 17973, 17970, 17969, 17968, 17967, 17966, 17963, 17962, 
    17961, 17960, 17959, 17956, 17955, 17954, 17953, 17952, 17949, 17948, 17947, 17946, 17945, 17942, 17941, 17940, 17939, 17938, 17935, 17934, 17933, 17932, 17931, 17928, 17927, 17926, 17925, 17924, 17921, 17920, 17919, 17918, 17917, 17914, 17913, 17912, 17911, 17910, 17907, 17906, 17905, 17904, 17903, 17900, 17899, 17898, 17896, 17893, 17892, 17889, 17886, 17885, 17884, 17883, 17882, 17879, 17878, 17877, 17876, 17875, 17872, 17871, 17870, 17869, 17868, 17865, 17864, 17863, 17862, 17861, 17858, 
    17857, 17856, 17855, 17854, 17851, 17850, 17849, 17848, 17847, 17844, 17843, 17842, 17841, 17840, 17837, 17836, 17835, 17834, 17833, 17830, 17829, 17828, 17827, 17826, 17823, 17822, 17821, 17820, 17819, 17816, 17815, 17814, 17813, 17812, 17809, 17808, 17807, 17806, 17805, 17802, 17801, 17800, 17799, 17798, 17795, 17794, 17793, 17792, 17791, 17788, 17787, 17786, 17785, 17784, 17781, 17780, 17779, 17778, 17777, 17774, 17773, 17772, 17771, 17770, 17767, 17766, 17765, 17764, 17763, 17760, 17759, 
    17758, 17757, 17756, 17753, 17752, 17751, 17750, 17749, 17746, 17745, 17744, 17743, 17742, 17739, 17738, 17737, 17736, 17735, 17732, 17731, 17730, 17729, 17728, 17725, 17724, 17723, 17722, 17721, 17718, 17717, 17716, 17715, 17714, 17711, 17710, 17709, 17708, 17707, 17704, 17703, 17702, 17701, 17700, 17697, 17696, 17695, 17694, 17693, 17690, 17689, 17688, 17687, 17686, 17683, 17682, 17681, 17680, 17679, 17676, 17675, 17674, 17673, 17672, 17669, 17668, 17667, 17666, 17665, 17662, 17661, 17660, 
    17659, 17658, 17655, 17654, 17653, 17652, 17651, 17648, 17647, 17646, 17645, 17644, 17641, 17640, 17639, 17638, 17637, 17634, 17633, 17632, 17631, 17630, 17627, 17626, 17625, 17624, 17619, 17618, 17617, 17616, 17613, 17612, 17611, 17610, 17609, 17606, 17605, 17604, 17603, 17602, 17599, 17598, 17597, 17596, 17595, 17592, 17591, 17590, 17589, 17588, 17585, 17584, 17583, 17582, 17581, 17578, 17577, 17576, 17575, 17574, 17571, 17570, 17569, 17568, 17567, 17564, 17563, 17562, 17561, 17560, 17557, 
    17556, 17555, 17554, 17553, 17550, 17549, 17548, 17547, 17546, 17543, 17542, 17541, 17540, 17539, 17536, 17535, 17534, 17533, 17529, 17528, 17527, 17522, 17521, 17520, 17519, 17518, 17515, 17514, 17513, 17512, 17511, 17508, 17507, 17506, 17505, 17504, 17501, 17500, 17499, 17498, 17497, 17494, 17493, 17492, 17491, 17490, 17487, 17486, 17485, 17484, 17483, 17480, 17479, 17478, 17477, 17476, 17473, 17472, 17471, 17470, 17469, 17466, 17465, 17464, 17463, 17462, 17459, 17458, 17457, 17456, 17455, 
    17452, 17451, 17450, 17449, 17448, 17445, 17444, 17443, 17442, 17441, 17438, 17437, 17436, 17435, 17434, 17431, 17430, 17429, 17428, 17427, 17424, 17423, 17422, 17421, 17420, 17417, 17416, 17415, 17414, 17413, 17410, 17409, 17408, 17407, 17406, 17403, 17402, 17401, 17400, 17399, 17396, 17395, 17394, 17393, 17392, 17389, 17388, 17387, 17386, 17385, 17382, 17381, 17380, 17379, 17378, 17375, 17374, 17373, 17372, 17371, 17368, 17367, 17366, 17365, 17364, 17361, 17360, 17359, 17358, 17357, 17354, 
    17353, 17352, 17351, 17350, 17347, 17346, 17345, 17344, 17343, 17340, 17339, 17338, 17337, 17336, 17333, 17332, 17331, 17330, 17329, 17326, 17325, 17324, 17323, 17322, 17319, 17318, 17317, 17316, 17315, 17312, 17311, 17310, 17309, 17308, 17305, 17304, 17303, 17302, 17301, 17298, 17297, 17296, 17295, 17294, 17291, 17290, 17289, 17288, 17287, 17284, 17283, 17282, 17281, 17280, 17277, 17276, 17275, 17274, 17269, 17268, 17267, 17266, 17263, 17262, 17261, 17260, 17259, 17256, 17255, 17254, 17253, 
    17252, 17249, 17248, 17247, 17246, 17245, 17242, 17241, 17240, 17239, 17238, 17235, 17234, 17233, 17232, 17231, 17228, 17227, 17226, 17225, 17224, 17221, 17220, 17219, 17218, 17217, 17214, 17213, 17212, 17211, 17210, 17207, 17206, 17205, 17204, 17203, 17200, 17199, 17198, 17197, 17196, 17193, 17192, 17191, 17190, 17189, 17186, 17185, 17184, 17183, 17182, 17179, 17178, 17177, 17176, 17175, 17172, 17171, 17170, 17169, 17168, 17165, 17164, 17163, 17162, 17158, 17157, 17156, 17155, 17154, 17151, 
    17150, 17149, 17148, 17147, 17144, 17143, 17142, 17141, 17140, 17137, 17136, 17135, 17134, 17133, 17130, 17129, 17128, 17127, 17126, 17123, 17122, 17121, 17120, 17119, 17116, 17115, 17114, 17113, 17112, 17109, 17108, 17107, 17106, 17105, 17102, 17101, 17100, 17099, 17098, 17095, 17094, 17093, 17092, 17091, 17088, 17087, 17086, 17085, 17084, 17081, 17080, 17079, 17078, 17077, 17074, 17073, 17072, 17071, 17070, 17067, 17066, 17065, 17064, 17063, 17060, 17059, 17058, 17057, 17056, 17053, 17052, 
    17051, 17050, 17049, 17046, 17045, 17044, 17043, 17042, 17039, 17038, 17037, 17036, 17035, 17032, 17031, 17030, 17029, 17028, 17025, 17024, 17023, 17022, 17021, 17018, 17017, 17016, 17015, 17014, 17011, 17010, 17009, 17008, 17007, 17004, 17003, 17002, 17001, 17000, 16997, 16996, 16995, 16994, 16993, 16990, 16989, 16988, 16987, 16986, 16983, 16982, 16981, 16980, 16979, 16976, 16975, 16974, 16973, 16972, 16969, 16968, 16967, 16966, 16965, 16962, 16961, 16960, 16959, 16958, 16955, 16954, 16953, 
    16952, 16951, 16948, 16947, 16946, 16945, 16944, 16941, 16940, 16939, 16938, 16937, 16934, 16933, 16932, 16931, 16930, 16927, 16926, 16925, 16924, 16923, 16920, 16919, 16918, 16917, 16916, 16913, 16912, 16911, 16910, 16909, 16906, 16905, 16904, 16903, 16902, 16899, 16898, 16897, 16896, 16895, 16892, 16891, 16890, 16889, 16884, 16883, 16882, 16881, 16878, 16877, 16876, 16875, 16874, 16871, 16870, 16869, 16868, 16867, 16864, 16863, 16862, 16861, 16860, 16857, 16856, 16855, 16854, 16853, 16850, 
    16849, 16848, 16847, 16846, 16843, 16842, 16841, 16840, 16839, 16836, 16835, 16834, 16833, 16832, 16829, 16828, 16827, 16826, 16825, 16822, 16821, 16820, 16819, 16818, 16815, 16814, 16813, 16812, 16811, 16808, 16807, 16806, 16805, 16804, 16800, 16799, 16798, 16797, 16793, 16792, 16791, 16790, 16787, 16786, 16785, 16784, 16783, 16780, 16779, 16778, 16777, 16776, 16773, 16772, 16771, 16770, 16769, 16766, 16765, 16764, 16763, 16762, 16759, 16758, 16757, 16756, 16755, 16752, 16751, 16750, 16749, 
    16748, 16745, 16744, 16743, 16742, 16741, 16738, 16737, 16736, 16735, 16734, 16731, 16730, 16729, 16728, 16727, 16724, 16723, 16722, 16721, 16720, 16717, 16716, 16715, 16714, 16713, 16710, 16709, 16708, 16707, 16706, 16703, 16702, 16701, 16700, 16699, 16696, 16695, 16694, 16693, 16692, 16689, 16688, 16687, 16686, 16685, 16682, 16681, 16680, 16679, 16678, 16675, 16674, 16673, 16672, 16671, 16668, 16667, 16666, 16665, 16664, 16661, 16660, 16659, 16658, 16657, 16654, 16653, 16652, 16651, 16650, 
    16647, 16646, 16645, 16644, 16643, 16640, 16639, 16638, 16637, 16636, 16633, 16632, 16631, 16630, 16629, 16626, 16625, 16624, 16623, 16622, 16619, 16618, 16617, 16616, 16615, 16612, 16611, 16610, 16609, 16608, 16605, 16604, 16603, 16602, 16601, 16598, 16597, 16596, 16595, 16594, 16591, 16590, 16589, 16588, 16587, 16584, 16583, 16582, 16581, 16580, 16577, 16576, 16575, 16574, 16573, 16570, 16569, 16568, 16567, 16566, 16563, 16562, 16561, 16560, 16559, 16556, 16555, 16554, 16553, 16552, 16549, 
    16548, 16547, 16546, 16545, 16542, 16541, 16540, 16539, 16538, 16535, 16534, 16533, 16532, 16531, 16527, 16526, 16525, 16524, 16521, 16520, 16519, 16518, 16517, 16514, 16513, 16512, 16511, 16510, 16507, 16506, 16505, 16504, 16503, 16500, 16499, 16498, 16497, 16496, 16493, 16492, 16491, 16490, 16489, 16486, 16485, 16484, 16483, 16482, 16479, 16478, 16477, 16476, 16475, 16472, 16471, 16470, 16469, 16468, 16465, 16464, 16463, 16462, 16461, 16458, 16457, 16456, 16455, 16454, 16451, 16450, 16449, 
    16448, 16447, 16444, 16443, 16442, 16441, 16440, 16437, 16435, 16434, 16433, 16432, 16428, 16427, 16426, 16425, 16423, 16422, 16421, 16420, 16419, 16418, 16416, 16415, 16414, 16413, 16412, 16411, 16409, 16408, 16407, 16406, 16405, 16404, 16402, 16401, 16400, 16399, 16398, 16395, 16394, 16393, 16392, 16391, 16388, 16387, 16386, 16385, 16384, 16381, 16380, 16379, 16378, 16377, 16374, 16373, 16372, 16371, 16370, 16367, 16366, 16365, 16364, 16363, 16360, 16359, 16358, 16357, 16356, 16353, 16352, 
    16351, 16350, 16349, 16346, 16345, 16344, 16343, 16342, 16339, 16338, 16337, 16336, 16335, 16332, 16331, 16330, 16329, 16328, 16325, 16324, 16323, 16322, 16321, 16318, 16317, 16316, 16315, 16314, 16311, 16310, 16309, 16308, 16307, 16304, 16303, 16302, 16301, 16300, 16297, 16296, 16295, 16294, 16293, 16290, 16289, 16288, 16287, 16286, 16285, 16283, 16282, 16281, 16280, 16279, 16276, 16275, 16274, 16273, 16272, 16269, 16268, 16267, 16266, 16265, 16262, 16261, 16260, 16259, 16258, 16257, 16255, 
    16254, 16253, 16252, 16251, 16248, 16247, 16246, 16245, 16244, 16241, 16240, 16239, 16238, 16237, 16234, 16233, 16232, 16231, 16230, 16227, 16226, 16225, 16224, 16223, 16220, 16219, 16218, 16217, 16216, 16213, 16212, 16211, 16210, 16209, 16206, 16205, 16204, 16203, 16202, 16201, 16199, 16198, 16197, 16196, 16195, 16192, 16191, 16190, 16189, 16188, 16185, 16184, 16183, 16182, 16177, 16176, 16175, 16174, 16171, 16170, 16169, 16168, 16167, 16164, 16163, 16162, 16161, 16160, 16157, 16156, 16155, 
    16154, 16153, 16150, 16149, 16148, 16147, 16146, 16143, 16142, 16141, 16140, 16139, 16136, 16135, 16134, 16133, 16132, 16129, 16128, 16127, 16126, 16125, 16122, 16121, 16120, 16119, 16118, 16115, 16114, 16113, 16112, 16111, 16108, 16107, 16106, 16105, 16104, 16101, 16100, 16099, 16098, 16097, 16094, 16093, 16092, 16091, 16090, 16087, 16086, 16085, 16084, 16083, 16080, 16079, 16078, 16077, 16076, 16073, 16072, 16071, 16070, 16069, 16066, 16065, 16063, 16062, 16059, 16058, 16057, 16056, 16055, 
    16052, 16051, 16050, 16049, 16048, 16045, 16044, 16043, 16042, 16041, 16038, 16037, 16036, 16035, 16034, 16033, 16031, 16030, 16029, 16028, 16027, 16024, 16023, 16022, 16021, 16020, 16017, 16016, 16015, 16014, 16013, 16010, 16009, 16008, 16007, 16006, 16003, 16002, 16001, 16000, 15999, 15996, 15995, 15994, 15993, 15992, 15989, 15988, 15987, 15986, 15985, 15982, 15981, 15980, 15979, 15978, 15975, 15974, 15973, 15972, 15971, 15968, 15967, 15966, 15965, 15964, 15961, 15960, 15959, 15958, 15957, 
    15954, 15953, 15952, 15951, 15950, 15947, 15946, 15945, 15944, 15943, 15940, 15939, 15938, 15937, 15936, 15933, 15932, 15931, 15930, 15929, 15926, 15925, 15924, 15923, 15922, 15919, 15918, 15917, 15916, 15915, 15912, 15911, 15910, 15909, 15908, 15905, 15904, 15903, 15902, 15901, 15898, 15897, 15896, 15895, 15894, 15891, 15890, 15889, 15888, 15887, 15884, 15883, 15882, 15881, 15880, 15877, 15876, 15875, 15874, 15873, 15870, 15869, 15868, 15867, 15866, 15863, 15862, 15861, 15860, 15859, 15856, 
    15855, 15854, 15853, 15852, 15849, 15848, 15847, 15846, 15845, 15842, 15841, 15840, 15839, 15838, 15835, 15834, 15833, 15832, 15831, 15828, 15827, 15826, 15825, 15824, 15821, 15820, 15819, 15818, 15817, 15814, 15813, 15812, 15811, 15810, 15807, 15806, 15805, 15804, 15803, 15800, 15799, 15798, 15797, 15792, 15791, 15790, 15789, 15786, 15785, 15784, 15783, 15782, 15779, 15778, 15777, 15776, 15775, 15772, 15771, 15770, 15769, 15768, 15765, 15764, 15763, 15762, 15761, 15758, 15757, 15756, 15755, 
    15754, 15751, 15750, 15749, 15748, 15747, 15744, 15743, 15742, 15741, 15740, 15737, 15736, 15735, 15734, 15733, 15730, 15729, 15728, 15727, 15726, 15725, 15723, 15722, 15721, 15720, 15719, 15716, 15715, 15714, 15713, 15712, 15709, 15708, 15707, 15705, 15702, 15701, 15700, 15698, 15695, 15694, 15693, 15692, 15691, 15688, 15687, 15686, 15685, 15684, 15681, 15680, 15679, 15678, 15677, 15676, 15674, 15673, 15672, 15671, 15670, 15667, 15666, 15665, 15664, 15663, 15660, 15659, 15658, 15657, 15656, 
    15653, 15652, 15651, 15650, 15649, 15646, 15645, 15644, 15643, 15642, 15639, 15638, 15637, 15636, 15635, 15632, 15631, 15630, 15629, 15628, 15627, 15625, 15624, 15623, 15622, 15621, 15620, 15618, 15617, 15616, 15615, 15614, 15611, 15610, 15609, 15608, 15607, 15604, 15603, 15602, 15601, 15600, 15599, 15597, 15596, 15595, 15594, 15593, 15590, 15589, 15588, 15587, 15586, 15583, 15582, 15581, 15580, 15579, 15578, 15576, 15575, 15574, 15573, 15572, 15569, 15568, 15567, 15566, 15565, 15562, 15561, 
    15560, 15559, 15558, 15555, 15554, 15553, 15552, 15551, 15548, 15547, 15546, 15545, 15544, 15541, 15540, 15539, 15538, 15537, 15534, 15533, 15532, 15531, 15530, 15527, 15526, 15525, 15524, 15523, 15522, 15520, 15519, 15518, 15517, 15516, 15513, 15512, 15511, 15510, 15509, 15506, 15505, 15504, 15503, 15502, 15499, 15498, 15497, 15496, 15495, 15492, 15491, 15490, 15489, 15488, 15485, 15484, 15483, 15482, 15481, 15478, 15477, 15476, 15475, 15474, 15471, 15470, 15469, 15468, 15467, 15464, 15463, 
    15462, 15461, 15460, 15457, 15456, 15455, 15454, 15453, 15450, 15449, 15448, 15447, 15446, 15443, 15442, 15441, 15440, 15435, 15434, 15433, 15432, 15429, 15428, 15427, 15426, 15425, 15422, 15421, 15420, 15419, 15418, 15415, 15414, 15413, 15412, 15411, 15408, 15407, 15406, 15405, 15404, 15401, 15400, 15399, 15398, 15397, 15394, 15393, 15392, 15391, 15390, 15387, 15386, 15385, 15384, 15383, 15380, 15379, 15378, 15377, 15376, 15373, 15372, 15371, 15370, 15369, 15366, 15365, 15364, 15363, 15362, 
    15359, 15358, 15357, 15356, 15355, 15352, 15351, 15350, 15349, 15348, 15345, 15344, 15343, 15342, 15341, 15338, 15337, 15336, 15334, 15333, 15331, 15330, 15329, 15328, 15327, 15324, 15323, 15322, 15321, 15320, 15319, 15317, 15316, 15315, 15314, 15313, 15310, 15309, 15308, 15307, 15306, 15303, 15302, 15301, 15300, 15299, 15296, 15295, 15294, 15293, 15292, 15289, 15288, 15287, 15286, 15285, 15282, 15281, 15280, 15279, 15278, 15275, 15274, 15273, 15272, 15271, 15268, 15267, 15266, 15265, 15264, 
    15261, 15260, 15259, 15258, 15257, 15254, 15253, 15252, 15251, 15250, 15247, 15246, 15245, 15244, 15243, 15240, 15239, 15238, 15237, 15236, 15233, 15232, 15231, 15230, 15229, 15226, 15225, 15224, 15223, 15222, 15219, 15218, 15217, 15216, 15215, 15212, 15211, 15210, 15209, 15208, 15205, 15204, 15203, 15202, 15201, 15198, 15197, 15196, 15195, 15194, 15191, 15190, 15189, 15188, 15187, 15184, 15183, 15182, 15181, 15180, 15177, 15176, 15175, 15174, 15173, 15170, 15169, 15168, 15167, 15166, 15163, 
    15162, 15161, 15160, 15159, 15156, 15155, 15154, 15153, 15152, 15149, 15148, 15147, 15146, 15145, 15142, 15141, 15140, 15139, 15138, 15135, 15134, 15133, 15132, 15131, 15128, 15127, 15126, 15125, 15121, 15120, 15119, 15118, 15117, 15114, 15113, 15112, 15111, 15110, 15107, 15106, 15105, 15104, 15103, 15100, 15099, 15098, 15097, 15096, 15093, 15092, 15091, 15090, 15086, 15085, 15084, 15083, 15082, 15079, 15078, 15077, 15076, 15075, 15072, 15071, 15070, 15069, 15068, 15065, 15064, 15063, 15062, 
    15061, 15058, 15057, 15056, 15055, 15054, 15051, 15050, 15049, 15048, 15047, 15044, 15043, 15042, 15041, 15040, 15037, 15036, 15035, 15034, 15033, 15030, 15029, 15028, 15027, 15026, 15023, 15022, 15021, 15020, 15019, 15016, 15015, 15014, 15013, 15012, 15009, 15008, 15007, 15006, 15005, 15002, 15001, 15000, 14999, 14998, 14997, 14995, 14994, 14993, 14992, 14991, 14988, 14987, 14986, 14985, 14984, 14981, 14980, 14979, 14978, 14977, 14974, 14973, 14972, 14967, 14966, 14965, 14964, 14963, 14960, 
    14959, 14958, 14957, 14956, 14955, 14953, 14952, 14951, 14950, 14949, 14946, 14945, 14944, 14943, 14942, 14939, 14938, 14937, 14936, 14935, 14932, 14931, 14930, 14929, 14928, 14925, 14924, 14923, 14922, 14921, 14918, 14917, 14916, 14915, 14914, 14911, 14910, 14909, 14908, 14907, 14904, 14903, 14902, 14901, 14900, 14897, 14896, 14895, 14894, 14893, 14890, 14889, 14888, 14887, 14886, 14883, 14882, 14881, 14880, 14879, 14876, 14875, 14874, 14873, 14872, 14869, 14868, 14867, 14866, 14865, 14864, 
    14862, 14861, 14860, 14859, 14858, 14857, 14855, 14854, 14853, 14852, 14851, 14850, 14848, 14847, 14846, 14845, 14844, 14843, 14841, 14840, 14839, 14838, 14837, 14836, 14834, 14833, 14832, 14831, 14830, 14829, 14827, 14826, 14825, 14824, 14823, 14822, 14820, 14819, 14818, 14817, 14816, 14815, 14813, 14812, 14811, 14810, 14809, 14808, 14806, 14805, 14804, 14803, 14802, 14801, 14799, 14798, 14797, 14796, 14795, 14794, 14792, 14791, 14790, 14789, 14788, 14785, 14784, 14783, 14782, 14781, 14778, 
    14777, 14776, 14775, 14774, 14771, 14770, 14769, 14768, 14767, 14764, 14763, 14762, 14761, 14760, 14757, 14756, 14755, 14754, 14753, 14750, 14749, 14748, 14747, 14746, 14743, 14742, 14741, 14740, 14739, 14736, 14735, 14734, 14733, 14732, 14729, 14728, 14727, 14726, 14725, 14722, 14721, 14720, 14719, 14718, 14715, 14714, 14713, 14712, 14711, 14708, 14707, 14706, 14705, 14704, 14700, 14699, 14698, 14697, 14694, 14693, 14692, 14691, 14690, 14687, 14686, 14685, 14684, 14683, 14680, 14679, 14678, 
    14677, 14676, 14673, 14672, 14671, 14670, 14669, 14666, 14665, 14664, 14663, 14662, 14659, 14658, 14657, 14656, 14655, 14652, 14651, 14650, 14649, 14648, 14645, 14644, 14643, 14642, 14641, 14640, 14638, 14637, 14636, 14635, 14634, 14631, 14630, 14629, 14628, 14627, 14624, 14623, 14622, 14621, 14620, 14617, 14616, 14615, 14614, 14613, 14610, 14609, 14608, 14607, 14606, 14603, 14602, 14601, 14600, 14599, 14598, 14596, 14595, 14594, 14593, 14592, 14591, 14589, 14588, 14587, 14586, 14585, 14584, 
    14582, 14581, 14580, 14579, 14578, 14577, 14575, 14574, 14573, 14572, 14571, 14570, 14568, 14567, 14566, 14565, 14564, 14563, 14561, 14560, 14559, 14558, 14557, 14556, 14554, 14553, 14552, 14551, 14550, 14549, 14547, 14546, 14545, 14544, 14543, 14542, 14540, 14539, 14538, 14537, 14536, 14535, 14533, 14532, 14531, 14530, 14529, 14526, 14525, 14524, 14523, 14522, 14519, 14518, 14517, 14516, 14515, 14512, 14511, 14510, 14509, 14508, 14505, 14504, 14503, 14502, 14501, 14498, 14497, 14496, 14495, 
    14494, 14491, 14490, 14489, 14488, 14487, 14484, 14483, 14482, 14481, 14480, 14477, 14476, 14475, 14474, 14473, 14470, 14469, 14468, 14467, 14466, 14463, 14462, 14461, 14460, 14459, 14456, 14455, 14454, 14453, 14452, 14449, 14448, 14447, 14446, 14445, 14442, 14441, 14440, 14439, 14438, 14435, 14434, 14433, 14432, 14431, 14428, 14427, 14426, 14425, 14424, 14421, 14420, 14419, 14418, 14417, 14414, 14413, 14412, 14411, 14410, 14407, 14406, 14405, 14404, 14403, 14400, 14399, 14398, 14397, 14396, 
    14393, 14392, 14391, 14390, 14389, 14386, 14385, 14384, 14383, 14382, 14379, 14378, 14377, 14376, 14375, 14372, 14371, 14370, 14369, 14368, 14365, 14364, 14363, 14362, 14361, 14358, 14357, 14356, 14355, 14354, 14351, 14350, 14349, 14348, 14347, 14343, 14342, 14341, 14340, 14337, 14336, 14335, 14334, 14333, 14330, 14329, 14328, 14327, 14326, 14323, 14322, 14321, 14320, 14319, 14316, 14315, 14314, 14313, 14312, 14309, 14308, 14307, 14306, 14305, 14302, 14301, 14300, 14299, 14298, 14295, 14294, 
    14293, 14292, 14291, 14288, 14287, 14286, 14285, 14284, 14281, 14280, 14279, 14278, 14277, 14274, 14273, 14272, 14271, 14270, 14267, 14266, 14265, 14264, 14263, 14260, 14259, 14258, 14257, 14256, 14253, 14252, 14251, 14250, 14249, 14246, 14244, 14243, 14242, 14239, 14237, 14236, 14235, 14232, 14231, 14230, 14229, 14228, 14225, 14224, 14223, 14222, 14221, 14218, 14217, 14216, 14215, 14214, 14211, 14210, 14209, 14208, 14207, 14204, 14203, 14202, 14201, 14200, 14197, 14196, 14195, 14194, 14193, 
    14190, 14189, 14188, 14187, 14186, 14183, 14182, 14181, 14180, 14179, 14176, 14175, 14174, 14173, 14172, 14169, 14168, 14167, 14166, 14165, 14162, 14161, 14160, 14159, 14158, 14155, 14154, 14153, 14152, 14151, 14148, 14147, 14146, 14145, 14144, 14141, 14140, 14139, 14138, 14137, 14134, 14133, 14132, 14131, 14130, 14127, 14126, 14125, 14124, 14123, 14120, 14119, 14118, 14117, 14116, 14113, 14112, 14111, 14110, 14109, 14106, 14105, 14104, 14103, 14102, 14099, 14098, 14097, 14096, 14095, 14092, 
    14091, 14090, 14089, 14088, 14085, 14084, 14083, 14082, 14081, 14078, 14077, 14076, 14075, 14074, 14071, 14070, 14069, 14068, 14067, 14064, 14063, 14062, 14061, 14060, 14057, 14056, 14055, 14054, 14053, 14050, 14049, 14048, 14047, 14046, 14043, 14042, 14041, 14040, 14039, 14036, 14035, 14034, 14033, 14032, 14029, 14028, 14027, 14026, 14025, 14022, 14021, 14020, 14019, 14018, 14015, 14014, 14013, 14012, 14011, 14008, 14007, 14006, 14005, 14001, 14000, 13999, 13998, 13997, 13994, 13993, 13992, 
    13991, 13990, 13987, 13986, 13985, 13984, 13983, 13980, 13979, 13978, 13977, 13976, 13973, 13972, 13971, 13970, 13969, 13966, 13965, 13964, 13963, 13958, 13957, 13956, 13955, 13952, 13951, 13950, 13949, 13948, 13945, 13944, 13943, 13942, 13941, 13938, 13937, 13936, 13935, 13934, 13931, 13930, 13929, 13928, 13927, 13924, 13923, 13922, 13921, 13920, 13917, 13916, 13915, 13914, 13913, 13910, 13909, 13908, 13907, 13906, 13903, 13902, 13901, 13900, 13899, 13896, 13895, 13894, 13893, 13892, 13889, 
    13888, 13887, 13886, 13885, 13882, 13881, 13880, 13878, 13875, 13874, 13871, 13868, 13867, 13866, 13864, 13861, 13860, 13859, 13858, 13857, 13854, 13853, 13852, 13851, 13850, 13847, 13846, 13845, 13844, 13843, 13840, 13839, 13838, 13837, 13836, 13833, 13832, 13831, 13830, 13829, 13826, 13825, 13824, 13823, 13822, 13819, 13818, 13817, 13816, 13815, 13812, 13811, 13810, 13809, 13808, 13805, 13804, 13803, 13802, 13801, 13798, 13797, 13796, 13795, 13794, 13791, 13790, 13789, 13788, 13787, 13784, 
    13783, 13782, 13781, 13780, 13777, 13776, 13775, 13774, 13773, 13770, 13769, 13768, 13767, 13766, 13763, 13762, 13761, 13760, 13759, 13756, 13755, 13754, 13753, 13752, 13749, 13748, 13747, 13746, 13745, 13742, 13741, 13740, 13739, 13738, 13735, 13734, 13733, 13732, 13731, 13728, 13727, 13726, 13725, 13724, 13721, 13720, 13719, 13718, 13717, 13714, 13713, 13712, 13711, 13710, 13707, 13706, 13705, 13704, 13703, 13700, 13699, 13698, 13697, 13696, 13693, 13692, 13691, 13690, 13689, 13686, 13685, 
    13684, 13683, 13682, 13679, 13678, 13677, 13676, 13675, 13672, 13671, 13670, 13669, 13668, 13665, 13664, 13663, 13662, 13661, 13658, 13657, 13656, 13655, 13654, 13651, 13650, 13649, 13648, 13647, 13644, 13643, 13642, 13641, 13640, 13637, 13636, 13635, 13634, 13633, 13630, 13629, 13628, 13627, 13626, 13623, 13622, 13621, 13620, 13619, 13616, 13615, 13614, 13613, 13612, 13608, 13607, 13606, 13605, 13602, 13601, 13600, 13599, 13598, 13595, 13594, 13593, 13592, 13591, 13588, 13587, 13586, 13585, 
    13584, 13581, 13580, 13579, 13578, 13577, 13574, 13573, 13572, 13571, 13570, 13567, 13566, 13565, 13564, 13563, 13560, 13559, 13558, 13557, 13556, 13553, 13552, 13551, 13550, 13549, 13546, 13545, 13544, 13543, 13542, 13539, 13538, 13537, 13536, 13535, 13532, 13531, 13530, 13529, 13528, 13525, 13524, 13523, 13522, 13521, 13518, 13517, 13516, 13515, 13511, 13510, 13509, 13508, 13504, 13503, 13502, 13501, 13500, 13497, 13496, 13495, 13494, 13493, 13490, 13489, 13488, 13487, 13486, 13483, 13482, 
    13481, 13480, 13479, 13476, 13475, 13474, 13473, 13472, 13469, 13468, 13467, 13466, 13465, 13462, 13461, 13460, 13459, 13458, 13455, 13454, 13453, 13452, 13451, 13448, 13447, 13446, 13445, 13444, 13441, 13440, 13439, 13438, 13437, 13434, 13433, 13432, 13431, 13430, 13427, 13426, 13425, 13424, 13423, 13420, 13419, 13418, 13417, 13416, 13413, 13412, 13411, 13410, 13409, 13406, 13405, 13404, 13403, 13402, 13399, 13398, 13397, 13396, 13395, 13392, 13391, 13390, 13389, 13388, 13385, 13384, 13383, 
    13382, 13381, 13378, 13377, 13376, 13375, 13374, 13371, 13370, 13369, 13368, 13367, 13364, 13363, 13362, 13361, 13360, 13357, 13356, 13355, 13354, 13353, 13350, 13349, 13348, 13347, 13346, 13343, 13342, 13341, 13340, 13339, 13336, 13335, 13334, 13333, 13332, 13329, 13328, 13327, 13326, 13325, 13322, 13321, 13320, 13319, 13318, 13315, 13314, 13313, 13312, 13311, 13308, 13307, 13306, 13305, 13304, 13301, 13300, 13299, 13298, 13294, 13293, 13292, 13291, 13290, 13287, 13286, 13285, 13284, 13283, 
    13280, 13279, 13278, 13277, 13276, 13273, 13272, 13271, 13270, 13269, 13266, 13265, 13264, 13263, 13262, 13259, 13258, 13257, 13256, 13255, 13251, 13250, 13249, 13248, 13245, 13244, 13243, 13242, 13241, 13238, 13237, 13236, 13235, 13234, 13231, 13230, 13229, 13228, 13227, 13224, 13223, 13222, 13221, 13220, 13217, 13216, 13215, 13214, 13213, 13210, 13209, 13208, 13207, 13206, 13203, 13202, 13201, 13200, 13199, 13196, 13195, 13194, 13193, 13192, 13189, 13188, 13187, 13186, 13185, 13182, 13181, 
    13180, 13179, 13178, 13175, 13174, 13173, 13172, 13171, 13168, 13167, 13166, 13165, 13164, 13161, 13160, 13159, 13158, 13157, 13154, 13153, 13152, 13151, 13147, 13146, 13145, 13144, 13140, 13139, 13138, 13137, 13136, 13133, 13132, 13131, 13130, 13129, 13126, 13125, 13124, 13123, 13122, 13119, 13118, 13117, 13116, 13115, 13112, 13111, 13110, 13109, 13108, 13105, 13104, 13103, 13102, 13101, 13098, 13097, 13096, 13095, 13094, 13091, 13090, 13089, 13088, 13087, 13084, 13083, 13082, 13081, 13080, 
    13077, 13076, 13075, 13074, 13073, 13070, 13069, 13068, 13067, 13066, 13063, 13062, 13061, 13060, 13059, 13056, 13055, 13054, 13053, 13052, 13049, 13048, 13047, 13046, 13045, 13042, 13041, 13040, 13039, 13038, 13035, 13034, 13033, 13032, 13031, 13028, 13027, 13026, 13025, 13021, 13020, 13019, 13018, 13017, 13014, 13013, 13012, 13011, 13010, 13007, 13006, 13005, 13004, 13003, 13000, 12999, 12998, 12997, 12996, 12993, 12992, 12991, 12990, 12989, 12986, 12985, 12984, 12983, 12982, 12979, 12978, 
    12977, 12976, 12975, 12972, 12971, 12970, 12969, 12968, 12965, 12964, 12963, 12962, 12961, 12958, 12957, 12956, 12955, 12954, 12951, 12950, 12949, 12948, 12947, 12944, 12943, 12942, 12941, 12940, 12937, 12936, 12935, 12934, 12930, 12929, 12928, 12927, 12926, 12923, 12922, 12921, 12920, 12919, 12916, 12915, 12914, 12913, 12912, 12909, 12908, 12907, 12906, 12902, 12901, 12900, 12899, 12898)
    , value=c(72.45, 74.63, 74.07, 75.2, 73.95, 74.6, 76.51, 75.78, 76.1, 76.67, 76.2, 74.24, 70.52, 70.79, 69.19, 70.1, 70.07, 71.59, 73.62, 71.92, 70.85, 73.67, 71.84, 72.69, 67.91, 69.2, 65.8, 67.51, 68.41, 66.85, 66.38, 66.4, 68.52, 71.55, 70.33, 74.25, 70.16, 71.64, 68.83, 62.85, 63.96, 63.39, 61.01, 58.39, 57.55, 58.9, 61.93, 62.61, 63, 64.84, 61.5, 59.37, 60.01, 61.31, 61.42, 59.38, 58.8, 55.87, 57, 56.13, 58.5, 59.44, 58.79, 60, 57.28, 56.31, 56.44, 57.21, 55.96, 53.83, 52.51, 52.59, 54.51, 54.21, 53.14, 
    57.11, 57.95, 56.44, 56.65, 57.2, 58.8, 60.71, 62.32, 63.49, 62.59, 63.5, 62.32, 64.4, 64.02, 61.77, 63.1, 63.41, 65.8, 63.27, 62.41, 63.42, 63.28, 63.31, 65.49, 66.9, 63.8, 65.96, 67.72, 69.9, 69.96, 73.97, 73.78, 75.42, 74.09, 77.98, 77.94, 77.74, 76.94, 75.88, 73.2, 69.76, 69.61, 67.57, 66.73, 68.88, 68.24, 67.34, 68.62, 69.97, 68.96, 68.91, 70.43, 72.45, 70.56, 70.78, 72.5, 73.07, 76.46, 76.57, 75.1, 75.21, 76.66, 76.23, 77.2, 79.8, 78.57, 77.04, 78.5, 77.3, 75.4, 75.36, 75.88, 77.2, 79.06, 
    78.66, 79.41, 78.78, 79.36, 79.58, 79.93, 80.66, 80.3, 81.67, 82, 81.79, 82.65, 83.41, 85.66, 85.45, 83.78, 84.74, 81.63, 80.62, 80.86, 81.82, 79.8, 80.7, 81.45, 83.11, 81.86, 82.51, 84.89, 85.3, 84.43, 82.76, 81.3, 80.88, 82.1, 82.93, 83.76, 81.12, 81.73, 81.62, 83.29, 83.7, 83.91, 84.08, 85.64, 86.03, 86, 85, 85.6, 85.25, 85.21, 88, 90.01, 87.85, 88.05, 88.85, 88.58, 86.87, 87.95, 86.8, 84.55, 83.9, 83.97, 82.64, 83.41, 84.41, 83.2, 84.62, 86.81, 88.7, 90.92, 90.77, 92.34, 91.29, 91.82, 90.84, 
    88.98, 88.18, 86.78, 86.35, 85.88, 85.83, 87.05, 86.26, 86.15, 86.29, 85.81, 87.69, 87.58, 89.57, 88.13, 88.21, 89.09, 86.49, 87.55, 90.95, 90.85, 94.51, 93.23, 91.92, 92.93, 93.62, 90.72, 88.22, 86.14, 83.35, 83.86, 81.64, 82.86, 78.52, 78.95, 80.77, 80.38, 83, 83.13, 82.63, 84.79, 85.8, 87.25, 89.43, 89.65, 88.04, 88.93, 87.14, 88.93, 88.57, 89.06, 87.51, 85.59, 84.96, 84.5, 85.15, 88.52, 85.63, 87.65, 86.68, 86.24, 86.81, 88.56, 89.86, 91.74, 94.39, 95.15, 92.91, 94.11, 94.39, 96.27, 97.47, 
    96.75, 97.01, 94.98, 96, 91.75, 90.8, 90.02, 89.4, 88.13, 85.4, 90.18, 86.63, 87.38, 85.18, 85.57, 85.27, 86.65, 89.73, 92.99, 96.83, 95.4, 94.76, 92.87, 89.96, 89.27, 90.1, 93.8, 95.88, 96.9, 94.79, 93.84, 93.45, 97.12, 95.11, 93.33, 95.13, 91.51, 88.62, 89.35, 90.44, 88.49, 87.59, 87.9, 87.96, 90.9, 90.65, 92.65, 90.13, 87.21, 86.94, 86.81, 82.28, 79.62, 81.8, 82.6, 81.86, 81.42, 77.21, 75.07, 77.2, 77.76, 76.64, 78.38, 79.1, 75.55, 76.24, 75.4, 80.42, 83.67, 79.4, 82.36, 84.13, 86.08, 86.85, 
    86.85, 85.6, 86.87, 84.69, 83.68, 85.2, 86.19, 88.99, 89.81, 87.73, 88.93, 88.19, 88.61, 87.17, 87.98, 84.88, 84.9, 81.39, 78.59, 78.97, 78.69, 75.87, 73.87, 74.28, 72.47, 72.4, 73.41, 76.65, 75.23, 75.84, 73.05, 72.76, 76.06, 77.49, 76.36, 76.28, 76.7, 76.72, 79.97, 81.21, 80.21, 75.79, 77.11, 72.32, 68.72, 66.87, 67.29, 67.77, 67.51, 68.02, 68.84, 66.71, 66.34, 66.77, 69.85, 68.96, 67.07, 66.92, 65.94, 66.73, 65.73, 65.15, 67.96, 70.33, 65.77, 70.44, 69.79, 71.14, 71.1, 73.27, 71.85, 72.54, 
    69.75, 71.82, 66.08, 67.24, 69.03, 69.88, 74.45, 77.89, 80.79, 80.03, 80.81, 86.66, 90.31, 89.31, 89.24, 89.29, 92.17, 98.01, 96.04, 95.8, 92.08, 90.78, 88.87, 87.55, 85.92, 85.93, 83.81, 84.76, 84.19, 83.99, 81.95, 80.58, 78.55, 78.96, 76.14, 76.68, 76.37, 76.3, 78.11, 78.84, 83.65, 84.94, 85.38, 83.97, 83.86, 85.65, 84.36, 82.79, 84.92, 83.22, 83.19, 84.55, 85.58, 90.16, 88.35, 87.4, 85.05, 83.43, 84.13, 81.88, 84.73, 84, 82.37, 83, 86.2, 84.15, 81.54, 81.86, 81.01, 79.81, 81.31, 81.43, 86.87, 
    86.34, 86.08, 84.02, 83.97, 84.2, 84.76, 81.4, 81.32, 78.15, 80.39, 83.18, 84.64, 91.72, 89.56, 88.48, 88.26, 88.83, 87.34, 87.02, 91.54, 88.91, 88.31, 88.19, 83.04, 84.45, 82.68, 81.01, 82.71, 83.46, 88.99, 86.44, 87.82, 80.2, 79.97, 77.44, 79.01, 77.95, 80.09, 79.94, 77.18, 78.05, 78.5, 78.49, 76.48, 78.31, 81.7, 80.81, 78.6, 78.24, 76.6, 80.67, 78.39, 78.89, 79.89, 78.16, 77.43, 78.28, 76.76, 76.41, 73.18, 68.51, 58.3, 65.1, 67.35, 68.49, 68.85, 82.21, 88.14, 87.03, 95.07, 89.77, 89.68, 89.47, 
    86.44, 89.86, 91.14, 91.76, 92.87, 90.78, 90.79, 96.93, 96.7, 96.45, 94.81, 94.21, 89.52, 89.24, 89.22, 89.76, 88.66, 87.45, 84.02, 84.47, 85.59, 82.09, 82.67, 80.58, 82.08, 80.56, 80.01, 81.3, 80.09, 85.42, 86.74, 87.58, 84.91, 84.01, 80.65, 80.16, 80.36, 79.29, 76.92, 76.31, 74.46, 76.83, 80.94, 80.09, 74.02, 85.71, 81.19, 80.12, 82.72, 84.37, 80.88, 89.41, 85.34, 81.65, 78.64, 80.25, 77.2, 75.73, 74.54, 73.12, 74.79, 73.23, 69.49, 70.22, 69.65, 69.38, 67.45, 67.83, 66.22, 63.58, 64.02, 63.48, 
    60.75, 60.96, 59.73, 60.18, 60.15, 59.79, 57.29, 59.08, 58.94, 60.27, 60.16, 59.35, 58.64, 58.37, 58.14, 54.92, 58.92, 59.79, 61.79, 59.45, 59.34, 59.58, 58.76, 60.81, 59.58, 65.16, 63.82, 62.45, 62.16, 63.28, 62.29, 64.72, 63.29, 60.89, 60.94, 60.5, 61.02, 59.82, 59.63, 60.18, 60.16, 61.37, 61.22, 63.04, 62.74, 62.28, 62.61, 61.63, 61.83, 60.42, 61.07, 61.08, 59.32, 57.19, 56.87, 56.97, 55.67, 54.72, 53.84, 57.45, 57.56, 58.52, 55.74, 56.63, 58.14, 57.77, 56.98, 57.02, 56.34, 55.82, 54.55, 54.79, 
    53.69, 54.41, 54.2, 53.28, 53.57, 51.26, 51.16, 52.51, 51.59, 52.81, 53.28, 53.37, 53.78, 53.26, 52.12, 54.67, 52.77, 53.03, 54.44, 58.28, 57.76, 58.06, 56.78, 56.04, 55.9, 55.48, 55.49, 55.03, 53.76, 52.78, 52.26, 51.28, 51.72, 51.76, 53.29, 53.07, 54.15, 53.9, 52.58, 51.97, 50.47, 50.73, 51.94, 52.97, 52.24, 51.58, 52.39, 54.22, 53.83, 53.41, 52.43, 53.41, 50.35, 53.74, 56.97, 57.23, 55.04, 55.85, 53.55, 52.72, 50.93, 50.41, 49.91, 49.06, 49.9, 49.31, 48.51, 48.28, 47.78, 47.67, 47.38, 47.51, 
    46.32, 45.29, 44.74, 44.8, 44.55, 44.2, 44.24, 44.86, 44.03, 43.85, 44.23, 44.6, 42.81, 42.81, 42.89, 42.4, 42.2, 42.09, 40.71, 41.96, 41.78, 43.18, 42.31, 42.74, 43.34, 41.96, 42.73, 43.19, 42.27, 41.87, 40.98, 39.47, 39.36, 38.51, 37.82, 38.69, 37.45, 37.6, 38.57, 39.45, 38.97, 38.26, 37.7, 38.61, 38.4, 39.13, 39.81, 40.28, 39, 39.56, 38.49, 38.84, 38.43, 37.49, 37.65, 35.19, 33.08, 33.18, 34.17, 33.51, 33.56, 33.39, 34.45, 34.32, 33.12, 33.3, 31.84, 31.96, 33.76, 33.88, 34.88, 34.76, 35.14, 
    34.97, 33.83, 33.15, 33.89, 32.94, 32.42, 33.25, 33.66, 32.41, 32.15, 31.39, 31.14, 31.36, 32.21, 32.03, 32.43, 31.27, 30.98, 31.36, 30.16, 30.02, 30.07, 30.57, 29.46, 30.01, 29.33, 29.6, 28.59, 28.54, 28.04, 28.04, 27.67, 27.15, 26.75, 27.59, 27.04, 27.79, 26.68, 26.32, 26.52, 26.64, 26.97, 25.85, 26.43, 25.57, 24.86, 24.15, 24.19, 24.15, 23.52, 24.55, 24.35, 25.98, 24.68, 24.06, 24.92, 25.49, 25.4, 25.48, 26.28, 25.74, 26.4, 26.24, 26.88, 27.44, 27.34, 27.49, 27.59, 27.07, 27.5, 27.36, 28.28, 
    26.75, 27.4, 27.12, 28.47, 27.05, 28.68, 29.13, 30.71, 30.53, 31.2, 28.99, 29.15, 27.94, 27.53, 27.81, 28.13, 29.53, 29.06, 28.61, 29.53, 30.38, 29.23, 29.48, 29.46, 28.32, 26.48, 26.75, 27.08, 27.41, 27.17, 26.36, 26.3, 26.87, 27.08, 27.6, 27.32, 27.3, 27.69, 27.75, 27.08, 27.22, 26.48, 27.13, 26.67, 25.91, 27.27, 28.23, 27.53, 27.51, 27.1, 28.76, 27.67, 29.7, 30.46, 30.14, 29.78, 29.37, 30.06, 30.12, 30.43, 28.64, 28.09, 28.42, 27.68, 27.35, 25.46, 25.92, 26.14, 26.15, 25.28, 24.92, 25.23, 
    23.52, 23.55, 22.93, 22.78, 23.04, 23.68, 23.24, 23.48, 24.02, 22.98, 22.85, 22.84, 21.75, 22.18, 22.04, 22.13, 22.4, 22.38, 22.19, 21.97, 22.06, 20.76, 21.14, 19.96, 19.62, 19.46, 19.31, 19.86, 20.17, 20.35, 19.83, 19.92, 20.18, 19.8, 20.39, 21, 21.04, 21.09, 21.53, 21.82, 21.45, 20.64, 22.15, 22.48, 21.69, 20.02, 20.57, 21.86, 21.93, 21.3, 21.17, 18.73, 18.82, 17.84, 18.42, 17.78, 17.11, 18.06, 18.21, 17.5, 16.28, 16.84, 17.19, 16.12, 19.05, 19.98, 22.38, 22.96, 24.34, 24.5, 23.68, 23.83, 24.21, 
    24.24, 23.77, 23.93, 24.02, 24.02, 24.69, 24.62, 25, 26.03, 26.06, 26.13, 25.56, 25.47, 24.71, 24.82, 24.31, 23.74, 23.58, 23.75, 23.98, 24.19, 23.78, 23.63, 24.31, 24.17, 24.43, 25.1, 25.05, 24.87, 25.21, 25.55, 25.45, 25.7, 25.97, 25.37, 25.04, 24.37, 24.66, 24.73, 25.2, 24.6, 25.06, 24.74, 25.5, 24.9, 25.18, 25.63, 27.25, 26.62, 26.62, 27.08, 27.21, 27.38, 27.13, 26.61, 25.52, 24.71, 25.79, 25.19, 25.68, 25.87, 25.68, 25.43, 25.48, 24.74, 25.06, 25.94, 25.73, 25.84, 25.11, 25.16, 25.31, 24.66, 
    24.75, 24.17, 24.13, 24.57, 24.67, 25.1, 24.83, 25.65, 25.56, 25.65, 25.52, 26.24, 26.37, 26.02, 26.35, 26.76, 26.25, 25.93, 25.8, 26.28, 25.59, 26.52, 26.83, 26.8, 27, 27.23, 26.64, 25.06, 25.36, 24.18, 23.6, 23.5, 24.35, 23.91, 24.17, 25.2, 26.05, 25.76, 26.34, 26.69, 26.26, 26.58, 26.84, 27.59, 26.98, 26.47, 27.24, 28.07, 27.38, 27.42, 27.27, 27.69, 25.97, 26.05, 26.48, 26.47, 26.21, 26.22, 27.37, 27.55, 27.11, 26.53, 26.97, 26.24, 26.81, 27.17, 27.42, 27.73, 27.15, 27.2, 28.12, 28.3, 27.91, 
    29.36, 29.78, 29.56, 29.7, 30.04, 30.61, 30.83, 29.38, 29.29, 29.85, 29.75, 30.51, 30.7, 31.33, 30.5, 30.38, 29.28, 29.98, 29.98, 30.56, 30.26, 29.71, 29.65, 27.9, 28.16, 27.67, 27.28, 27.78, 27.98, 28.17, 27.5, 28.15, 28.65, 27.64, 27.53, 26.42, 26.2, 26.07, 26.22, 26.12, 26.15, 26.05, 25.92, 26.11, 26.36, 25.66, 25.09, 25.28, 25.58, 24.74, 25.45, 26.28, 26.51, 26.46, 26.61, 26.44, 27.03, 27.34, 26.35, 26.16, 25.96, 26.56, 26.96, 26.87, 26.03, 26.62, 27.57, 27.99, 27.47, 26.42, 26.29, 25.79, 
    26.89, 27.43, 27.55, 27.09, 28.54, 28.66, 28.8, 28.14, 28.71, 28.25, 28.05, 27.82, 28.58, 27.41, 26.84, 25.58, 25.9, 25.72, 24.45, 23.25, 23.16, 22.82, 23.55, 23.15, 22.84, 22.23, 21.99, 22.28, 23.02, 22.53, 23.22, 23.92, 24.2, 23.72, 23.8, 23.78, 24.52, 24.76, 23.6, 24.42, 24.6, 23.73, 23.13, 22.7, 21.08, 20.65, 20.43, 20.32, 22.04, 21.81, 21.6, 22.04, 21.37, 22.51, 22.25, 23.97, 23.91, 25.02, 25.24, 24.74, 24.63, 23.55, 23.9, 24.72, 25.08, 24.5, 25.68, 25.85, 26.47, 26.94, 26.25, 26.63, 25.39, 
    25.18, 24.4, 24.33, 24.52, 23.96, 23.93, 24.78, 24.22, 25.66, 25.28, 27.37, 27.06, 27.02, 27.08, 27.25, 26.97, 26.53, 26.67, 26.42, 26.69, 25.76, 24.65, 23.81, 22.52, 23.22, 22.6, 22.36, 22.03, 22.99, 22.85, 22.7, 22.23, 21.5, 21.82, 22.02, 22.4, 23.14, 22.69, 21.62, 21.08, 21.31, 21.13, 21.78, 22.26, 22.7, 21.65, 21.75, 20.77, 19.69, 19.31, 19.18, 17.62, 18.49, 18.13, 18.91, 20.59, 21.41, 21.9, 21.8, 21.92, 22.64, 22.62, 22.27, 22.53, 22.09, 24.21, 23.88, 23.65, 25.33, 26.48, 26.1, 25.18, 24.96, 
    24.76, 24.96, 24.63, 24, 23.42, 24.27, 25.29, 24.88, 24.72, 24.09, 22.83, 23.46, 22.42, 21.29, 25.37, 26.66, 27.42, 25.33, 23.57, 22.44, 22.25, 22.28, 23.2, 23.29, 23.19, 22.86, 23.45, 22.83, 22.47, 21.82, 21.31, 20.44, 20.04, 19.86, 19.95, 20, 19.9, 19.73, 19.42, 19.22, 19.36, 19.42, 19.53, 19.53, 19.69, 19.34, 18.99, 19.09, 19.23, 19.28, 19.01, 19.09, 18.77, 18.56, 18.11, 17.74, 17.59, 17.69, 17.72, 17.95, 17.67, 17.58, 17.28, 17.25, 17.07, 16.65, 16.62, 16.51, 16.52, 16.78, 16.55, 16.54, 16.61, 
    16.31, 15.98, 15.69, 16.05, 15.98, 16.34, 16.77, 16.61, 16.96, 17.2, 17.37, 17.31, 17.11, 17.42, 16.55, 16.16, 17.02, 17.47, 17.47, 17.17, 17.45, 17.15, 17.08, 16.68, 16.38, 16.39, 16.25, 15.38, 15.7, 15.68, 15.66, 15.05, 14.63, 14.65, 14.04, 13.98, 14.08, 14.41, 14.6, 14.58, 14.51, 14.26, 14.22, 13.87, 14.02, 14.42, 14.84, 14.68, 14.92, 14.84, 14.44, 14.24, 14.16, 14.11, 13.76, 13.41, 13.83, 14.06, 14.04, 13.75, 14.38, 13.61, 13.23, 12.96, 13.27, 12.11, 11.62, 11.73, 11.74, 11.79, 12.11, 11.76, 
    11.79, 11.75, 11.27, 11.1, 10.99, 10.77, 10.62, 10.73, 10.77, 10.25, 10.43, 10.34, 10.18, 10.34, 10.5, 10.13, 10.16, 10.22, 10.52, 10.05, 9.79, 9.69, 9.56, 9.36, 9.63, 9.53, 9.85, 9.85, 9.46, 9.58, 9.67, 9.82, 10.02, 9.57, 9.31, 9.25, 8.89, 8.58, 8.45, 8.2, 8.26, 8.21, 8.28, 8.19, 8.07, 8.19, 8.18, 8.24, 8.22, 8.6, 8.64, 8.6, 8.62, 8.45, 8.24, 7.97, 7.86, 7.65, 7.56, 7.55, 7.61, 7.64, 7.58, 7.79, 7.72, 7.87, 8, 8.13, 7.97, 8.14, 8.04, 8.15, 8.21, 8.12, 7.83, 7.85, 7.9, 7.93, 7.95, 8.15, 7.85, 
    7.81, 7.86, 8.01, 8.18, 8.22, 8.36, 8.32, 8.1, 7.95, 7.81, 7.58, 7.61, 7.64, 7.84, 7.91, 7.87, 8, 8.08, 8.24, 7.84, 7.78, 7.78, 7.87, 7.85, 7.87, 7.48, 7.52, 7.42, 7.44, 7.52, 7.46, 7.59, 7.48, 7.46, 7.51, 7.78, 7.14, 7.05, 7.4, 7.52, 7.22, 7.44, 7.6, 7.6, 7.36, 7.37, 7.56, 7.4, 7.19, 7, 6.51, 6.43, 6.54, 6.62, 6.64, 6.7, 6.69, 6.55, 6.54, 6.37, 6.34, 6.41, 6.41, 6.39, 6.13, 6.12, 5.99, 5.96, 5.92, 5.77, 5.77, 5.86, 5.94, 5.93, 5.8, 5.73, 5.69, 5.65, 5.76, 5.67, 5.64, 5.6, 5.75, 5.84, 5.85, 5.82, 
    5.82, 5.76, 5.88, 5.73, 5.8, 5.74, 5.63, 5.43, 5.51, 5.53, 5.42, 5.46, 5.33, 5.33, 5.16, 5.25, 5.25, 5.26, 5.35, 5.31, 5.26, 5.33, 5.32, 5.4, 5.3, 5.42, 5.43, 5.26, 5.35, 5.55, 5.54, 5.45, 5.35, 5.53, 5.57, 5.58, 5.37, 5.3, 5.13, 5.29, 5.22, 5.13, 4.95, 4.91, 4.76, 4.83, 4.72, 4.82, 4.89, 4.79, 4.94, 4.87, 4.77, 4.81, 4.57, 4.94, 4.93, 4.98, 4.87, 5.02, 4.94, 5.12, 5.22, 5.24, 5.32, 5.31, 5.24, 5.15, 5.25, 5.43, 5.18, 4.98, 5.21, 5.04, 5.27, 5.11, 5.08, 4.97, 5.11, 5.32, 5.31, 5.28, 5.33, 5.48, 
    5.49, 5.54, 5.45, 5.5, 5.51, 5.46, 5.58, 5.72, 5.83, 5.94, 5.81, 6.26, 5.57, 5.53, 5.73, 5.7, 5.41, 5.39, 5.43, 5.31, 5.28, 5.42, 5.48, 5.24, 5.45, 5.62, 5.55, 5.5, 5.43, 5.49, 5.56, 5.61, 5.69, 5.34, 4.91, 5.19, 4.97, 5.07, 5.31, 5.42, 5.19, 4.83, 4.99, 4.69, 5.03, 5.03, 5.51, 5.49, 5.25, 5.03, 5.27, 5.7, 5.41, 6.11, 6.54, 6.34, 6.32, 6.32, 6.22, 6.07, 5.8, 5.23, 5.09, 4.93, 4.84, 5.01, 4.79, 4.87, 4.46, 4.61, 4.3, 4.5, 4.37, 4.3, 4.46, 4.58, 4.56, 4.74, 5, 5.34, 5.39, 5.51, 5.48, 5.58, 5.9, 
    5.55, 5.74, 5.41, 5.67, 5.92, 6.13, 6.15, 6.23, 6.41, 6.5, 6.24, 6.03, 5.9, 5.88, 5.81, 5.94, 5.81, 5.81, 5.89, 5.58, 5.67, 5.95, 5.87, 5.81, 5.65, 5.52, 5.43, 5.66, 5.69, 5.86, 5.48, 5.21, 5.31, 4.96, 5.02, 4.95, 4.43, 4.62, 4.54, 4.42, 4.21, 4.16, 4.4, 4.36, 4.14, 3.98, 4.02, 4.03, 4.08, 4.08, 4.01, 4.13, 3.93, 4.08, 4.37, 4.46, 4.54, 4.69, 4.69, 4.7, 4.6, 4.7, 4.89, 4.76, 4.68, 4.48, 4.69, 4.8, 4.89, 4.87, 4.76, 4.87, 4.94, 4.72, 4.68, 4.62, 4.4, 4.37, 4.41, 4.47, 4.52, 4.5, 4.58, 4.55, 4.64, 
    4.68, 4.66, 4.84, 4.92, 4.77, 4.78, 4.62, 4.42, 4.53, 4.57, 4.58, 4.7, 4.96, 4.61, 4.46, 4.51, 4.68, 4.76, 4.95, 5.63, 5.67, 5.54, 5.84, 5.66, 5.7, 5.89, 5.84, 5.84, 5.94, 6.1, 6.09, 6.1, 6.19, 5.93, 6.01, 5.95, 6.08, 6.1, 6.02, 6.01, 5.85, 5.78, 5.72, 5.95, 5.98, 6.05, 6.04, 6.1, 5.84, 5.8, 6.01, 5.89, 5.69, 5.85, 6.19, 6.12, 5.98, 6.1, 6.17, 6.33, 6.83, 6.61, 5.89, 5.96, 5.74, 5.54, 5.56, 5.46, 5.47, 5.6, 5.53, 5.58, 5.57, 5.41, 5.27, 5.3, 5.23, 5.32, 5.16, 5.2, 4.95, 4.77, 4.84, 4.79, 4.81, 
    4.86, 4.93, 4.99, 4.95, 4.85, 4.85, 4.98, 4.9, 5.07, 5.01, 5.09, 4.92, 4.88, 4.95, 4.99, 4.99, 4.98, 5.06, 4.85, 4.89, 5.4, 5.15, 5.24, 5.07, 4.67, 4.79, 5.05, 4.73, 4.87, 4.95, 5.23, 5.54, 5.6, 5.61, 5.81, 5.68, 6.04, 6.06, 5.9, 6.07, 5.87, 6.32, 6.17, 6.31, 6.81, 6.71, 6.67, 7.08, 7.24, 7.1, 7.12, 7.41, 7.54, 7.74, 7.99, 8.04, 8.22, 8.21, 8.27, 8.31, 8.19, 8.22, 8.25, 8.19, 8.06, 8.07, 8.13, 8.19, 8.07, 8.07, 8.36, 8.4, 8.41, 8.41, 8.52, 8.59, 8.48, 8.56, 8.58, 8.58, 8.58, 8.62, 8.65, 8.56, 
    8.51, 8.63, 8.58, 8.61, 8.53, 8.39, 8.37, 8.44, 8.44, 8.31, 8.4, 8.46, 8.39, 8.44, 8.59, 8.63, 8.67, 8.56, 8.6, 8.65, 8.62, 8.47, 8.44, 8.46, 8.34, 8.38, 8.41, 8.42, 8.32, 8.28, 8.33, 8.11, 8.09, 8.2, 8.19, 8.13, 8.15, 8.13, 7.96, 7.9, 7.98, 7.99, 8.05, 8, 7.96, 8.09, 8.21, 8.21, 8.15, 8.21, 8.24, 8.26, 8.25, 8.22, 8.06, 8.07, 8.15, 8.1, 7.99, 8.05, 8.09, 8.03, 8.08, 8.23, 8.15, 8.18, 8.34, 8.32, 8.25, 8.22, 8.3, 8.17, 8.17, 8.07, 7.9, 7.76, 7.82, 7.81, 7.88, 7.93, 7.85, 7.86, 8.04, 8, 8, 7.98, 
    8.05, 7.94, 7.94, 7.96, 7.72, 7.64, 7.74, 7.71, 7.77, 7.59, 7.46, 7.43, 7.44, 7.36, 7.42, 7.43, 7.47, 7.42, 7.33, 7.52, 7.58, 7.48, 7.48, 7.46, 7.41, 7.45, 7.46, 7.41, 7.51, 7.61, 7.5, 7.58, 7.56, 7.44, 7.4, 7.39, 7.48, 7.44, 7.24, 7.32, 7.18, 7.17, 7.22, 7.36, 7.3, 7.3, 7.35, 7.37, 7.6, 7.59, 7.55, 7.64, 7.59, 7.62, 7.53, 7.43, 7.53, 7.55, 7.58, 7.48, 7.39, 7.46, 7.35, 7.15, 7.28, 7.25, 7.09, 7.08, 7.13, 6.84, 6.87, 6.85, 6.8, 6.8, 6.94, 7.01, 7.12, 7.11, 7.15, 7.15, 7.14, 6.92, 6.88, 6.76, 
    6.95, 6.97, 7.03, 7.04, 7.04, 6.67, 6.74, 6.73, 6.49, 6.46, 6.41, 6.76, 6.82, 6.68, 6.8, 6.75, 7.02, 6.73, 6.95, 7.1, 7.06, 7.39, 7.47, 7.7, 7.32, 7.34, 7.49, 7.47, 7.65, 7.63, 7.39, 7.23, 7.1, 6.91, 6.95, 7, 6.93, 7.06, 7.13, 7.08, 7.06, 6.95, 6.84, 6.85, 6.8, 6.76, 7.32, 7.16, 7.21, 7.13, 7.12, 7.16, 7.29, 6.71, 6.71, 6.81, 6.78, 6.77, 6.9, 7.01, 7.25, 7.21, 7.25, 7.47, 7.37, 7.25, 7.11, 7.17, 7.08, 7.04, 6.99, 6.91, 6.89, 6.76, 6.66, 6.74, 6.56, 6.74, 6.66, 6.67, 6.66, 6.84, 6.89, 6.85, 7.07, 
    7.05, 7.04, 7.09, 7.19, 7.12, 7.04, 6.99, 6.95, 7.03, 7.01, 6.89, 6.61, 6.78, 6.84, 6.79, 6.71, 6.75, 6.62, 6.63, 6.47, 6.57, 6.34, 6.41, 6.41, 6.15, 6.27, 6.39, 6.32, 6.21, 6.17, 6.13, 6.12, 6.2, 6.14, 6.07, 6.04, 6.02, 6.1, 6.03, 5.72, 5.66, 5.66, 5.67, 5.79, 5.82, 5.75, 5.91, 5.8, 5.8, 5.65, 5.98, 6.01, 5.97, 5.88, 5.79, 5.91, 6.04, 6.1, 6.08, 6.12, 6.27, 6.26, 6.11, 6.32, 6.38, 6.39, 6.38, 6.43, 6.35, 6.29, 6.32, 6.35, 6.34, 6.41, 6.43, 6.32, 6.36, 6.21, 6.21, 6.09, 6.11, 5.96, 5.93, 6.19, 
    6.18, 6.22, 6.29, 6.26, 6.19, 6.11, 6.02, 6.17, 6.11, 6.03, 6.15, 6.15, 6.04, 5.98, 6.13, 6.02, 5.92, 5.86, 5.72, 5.66, 5.79, 5.73, 5.54, 5.67, 5.65, 5.99, 6.07, 6.01, 5.81, 5.76, 5.7, 5.71, 5.74, 5.79, 5.65, 5.54, 5.65, 5.7, 5.63, 5.66, 5.55, 5.36, 5.49, 5.53, 5.44, 5.54, 5.39, 5.43, 5.14, 5.05, 5.2, 5.2, 5.17, 5.09, 5.12, 5.16, 5.12, 4.84, 4.69, 4.79, 4.77, 5.1, 5.28, 5.3, 5.3, 5.24, 5.13, 5.12, 5.22, 5.21, 5.18, 5.41, 5.4, 5.41, 5.2, 5.06, 5.71, 5.66, 5.67, 5.54, 5.45, 5.53, 5.23, 5.31, 5.11, 
    4.93, 4.85, 4.97, 4.68, 4.85, 4.82, 5.04, 4.64, 4.34, 5.17, 5.8, 5.85, 5.86, 6.18, 6.01, 5.99, 5.75, 5.87, 6.29, 6.43, 6.5, 6.82, 6.89, 6.9, 6.8, 6.77, 6.81, 6.61, 7.06, 6.5, 6.48, 6.21, 6.99, 7.12, 6.97, 6.9, 6.73, 6.79, 6.57, 6.37, 6.34, 6.24, 6.4, 6.41, 6.43, 6.06, 5.8, 5.82, 5.5, 5.69, 5.48, 5.5, 5.35, 5.24, 5.01, 5.11, 5.02, 4.91, 5.05, 5.05, 4.8, 4.81, 4.62, 4.52, 4.5, 4.57, 4.66, 4.61, 4.69, 4.71, 4.93, 4.83, 4.91, 4.92, 4.99, 4.91, 4.78, 4.75, 4.93, 4.87, 4.89, 4.67, 4.8, 4.9, 4.88, 5.02, 
    4.9, 4.79, 4.64, 4.48, 4.48, 4.5, 4.36, 4.43, 4.47, 4.49, 4.4, 4.43, 4.43, 4.41, 4.49, 4.42, 4.34, 4.49, 4.58, 4.64, 4.64, 4.6, 4.48, 4.79, 4.77, 4.79, 4.55, 4.61, 4.8, 4.95, 5.08, 4.8, 4.99, 4.65, 4.6, 4.69, 4.57, 5.11, 5.16, 5.32, 4.94, 4.8, 4.6, 4.75, 4.78, 4.85, 4.95, 5.09, 5.19, 5.27, 5.14, 5.02, 5.39, 5.46, 5.37, 5.37, 5.41, 5.35, 5.35, 5.52, 5.66, 5.46, 5.39, 5.61, 5.25, 5.12, 5.3, 5.32, 4.95, 4.54, 4.4, 4.49, 4.55, 4.58, 4.59, 4.53, 4.41, 4.42, 4.51, 4.36, 4.34, 4.31, 4.34, 4.34, 4.34, 
    4.28, 4.3, 4.43, 4.5, 4.43, 4.49, 4.4, 4.37, 4.32, 4.31, 4.26, 4.3, 4.3, 4.27, 4.27, 4.23, 4.18, 4.16, 4.1, 4.1, 4.1, 4.03, 4.02, 4.07, 4.02, 4.14, 4.21, 4.26, 4.52, 4.66, 4.26, 4.21, 4.18, 4.4, 4.39, 4.25, 4.09, 4.35, 4.4, 4.35, 4.67, 4.55, 4.74, 4.38, 4.46, 4.16, 4, 4.07, 3.95, 3.86, 3.91, 3.87, 3.91, 3.77, 3.7, 3.6, 3.45, 3.51, 3.36, 3.28, 3.51, 3.56, 3.49, 3.65, 3.59, 3.47, 3.22, 3.33, 3.74, 3.44, 3.69, 3.86, 3.73, 3.04, 2.87, 3.07, 3.26, 3.05, 2.92, 2.98, 3.05, 2.84, 3.11, 3.02, 2.7, 3.03, 
    4.68, 4.7, 4.28, 4.23, 4.71, 5.12, 5.1, 4.97, 4.85, 4.87, 4.74, 4.88, 4.55, 4.42, 4.08, 4.35, 3.9, 3.45, 3.48, 3.71, 3.63, 3.45, 3.66, 3.88, 4.18, 4.24, 4.19, 4.14, 4.53, 4.57, 4.8, 4.37, 4.2, 4.47, 5.07, 5.17, 4.86, 4.56, 4.99, 5.06, 5.12, 5.1, 4.46, 4.36, 4.43, 4.09, 4.06, 4.29, 4.19, 4.21, 3.31, 3.69, 3.88, 4.07, 4, 4.21, 4.52, 5.3, 4.81, 5.09, 4.97, 5.44, 5.47, 5.88, 5.71, 5.72, 5.86, 6.02, 6.27, 6.46, 6.14, 6.2, 6.37, 6.45, 6.5, 6.84, 7.08, 6.92, 7, 7.17, 7.03, 6.7, 6.47, 6.57, 6.67, 6.75, 
    6.84, 7.07, 6.78, 6.39, 6.15, 5.72, 5.95, 6.2, 6.2, 6.58, 6.83, 6.85, 6.84, 7.01, 6.78, 6.77, 6.74, 6.71, 6.89, 7.12, 7.91, 8.4, 9.07, 8.32, 8.27, 8.22, 8.34, 8.25, 8.1, 8.04, 8.23, 8.13, 8.05, 7.86, 7.66, 7.65, 7.86, 7.87, 7.94, 8.04, 8.24, 7.96, 7.66, 7.85, 7.8, 7.77, 7.69, 7.86, 7.89, 7.81, 7.77, 7.6, 7.56, 7.84, 7.92, 7.93, 7.81, 7.6, 7.45, 7.22, 7.41, 7.63, 7.52, 7.4, 7.35, 7.44, 7.4, 7.75, 7.89, 7.7, 7.79, 8.33, 8.21, 8.2, 8.17, 8.22, 8.03, 7.64, 7.67, 7.93, 8.1, 8.18, 8.13, 8.12, 7.99, 
    7.88, 7.6, 7.66, 7.66, 7.44, 7.61, 7.45, 7.16, 7.1, 7.19, 7.27, 7.16, 7.06, 7.03, 6.92, 6.88, 6.54, 6.86, 6.92, 6.8, 7.14, 7.07, 7.08, 6.82, 7.09, 7.62, 7.51, 7.59, 7.59, 7.82, 7.87, 7.93, 7.99, 8.27, 8.21, 8.25, 8.07, 8.24, 8.2, 7.91, 7.89, 7.98, 7.98, 8.09, 7.5, 7.44, 7.5, 7.33, 7.23, 6.84, 6.71, 6.65, 6.62, 6.6, 6.45, 6.36, 6.38, 6.38, 6.38, 6.27, 6.4, 6.54, 6.68, 6.8, 6.78, 6.68, 6.88, 6.6, 6.33, 6.45, 6.5, 6.45, 6.56, 6.73, 6.65, 6.68, 6.74, 6.61, 6.6, 7.06, 7.12, 7.47, 7.48, 7.24, 7.22, 
    7.03, 7.07, 7.07, 7.32, 7.33, 7.2, 7.05, 6.79, 7.12, 7.06, 6.92, 6.78, 6.68, 6.08, 6.35, 6.21, 6.98, 6.71, 7.04, 7.12, 6.84, 6.87, 6.71, 7.26, 7.02, 7.62, 7.6, 7.83, 7.95, 7.62, 7.66, 7.9, 8.25, 8.4, 8.35, 8.62, 8.83, 8.65, 8.34, 8.8, 9.28, 9.19, 8.62, 8.93, 8.96, 8.54, 9.04, 8.77, 8.14, 7.89, 7.46, 7.71, 7.79, 8.12, 8.53, 8.49, 8.29, 8.53, 8.26, 7.84, 7.55, 7.97, 7.49, 7.33, 7.26, 6.86, 7.02, 7.07, 6.61, 6.48, 6.47, 6.73, 6.92, 6.75, 6.84, 6.51, 6.3, 6.43, 6.27, 6.28, 7.14, 6.97, 6.91, 7.42, 
    8.07, 8.07, 7.85, 7.71, 7.98, 8.54, 6.98, 6.75, 6.77, 6.45, 7.03, 7.54, 8.21, 7.84, 7.64, 7.21, 7.32, 7.31, 7.82, 7.93, 8.35, 7.98, 7.97, 7.69, 7.86, 8.42, 9.08, 8.88, 9.33, 9.63, 9.85, 10.01, 10.04, 10.11, 9.8, 9.87, 10.07, 9.93, 9.39, 9.66, 9.47, 9.85, 10.12, 10.37, 10.38, 10.07, 10.36, 10.49, 10.31, 10.14, 9.97, 10.25, 10.29, 10.36, 10.24, 10.64, 10.61, 10.66, 10.4, 10.4, 10.15, 10.02, 10.09, 10.66, 10.85, 10.42, 10.74, 10.81, 11.27, 11.25, 11.72, 11.82, 11.72, 12.06, 12.28, 12.13, 11.94, 
    11.81, 11.79, 12.16, 12.34, 12.09, 12.29, 12.51, 12.8, 12.84, 13.38, 13.18, 13.05, 12.88, 13.03, 12.78, 12.43, 12.36, 12.2, 12.67, 12.25, 12.34, 12.33, 12.13, 11.47, 11.3, 10.62, 10.58, 11.17, 11.3, 11.61, 11.88, 12.11, 12.37, 12.28, 12.75, 12.79, 12.84, 12.95, 12.64, 12.25, 12.08, 12.26, 12.15, 11.84, 12.25, 11.94, 12.54, 12.85, 13.01, 13.38, 13.24, 13.11, 13.36, 12.83, 13.32, 12.76, 12.07, 13.15, 14.54, 14.55, 15.02, 15.4, 15.82, 15.98, 16.21, 16.4, 16.37, 16.38, 16.21, 16.35, 16.39, 16.53, 
    16.46, 16.51, 16.69, 16.6, 16.05, 16.05, 16.05, 15.81, 15.99, 16.11, 16.19, 16.21, 16.55, 16.38, 16.52, 16.44, 16.56, 16.63, 16.66, 16.58, 16.7, 16.81, 17.03, 16.7, 16.77, 16.61, 16.52, 16.87, 16.5, 16.62, 16.41, 16.3, 16.69, 16.38, 16.25, 16.2, 16.36, 16.6, 16.58, 16.74, 16.62, 16.83, 16.75, 16.88, 16.66, 16.69, 16.79, 16.33, 16.06, 16.42, 16.42, 16.35, 16.76, 16.28, 16.71, 16.67, 16.02, 15.3, 15.3, 15.36, 15.31, 15.39, 15.5, 15.17, 15.2, 15.28, 15.3, 15.21, 15.05, 14.96, 15.02, 15.04, 14.63, 
    14.59, 14.46, 14.57, 14.67, 14.67, 14.47, 14.46, 14.49, 14.42, 14.49, 14.47, 14.76, 14.64, 14.76, 14.54, 14.51, 14.69, 14.68, 14.37, 14.49, 14.26, 14.15, 14.16, 14.39, 14.34, 14.27, 14.06, 14.03, 14.09, 14.01, 14.41, 14.47, 14.31, 14.21, 14.02, 14.02, 13.94, 14.06, 13.87, 13.86, 14.1, 13.96, 13.9, 13.98, 14.26, 14.34, 14.46, 14.53, 14.6, 14.59, 14.53, 14.67, 14.79, 14.87, 14.75, 14.67, 14.84, 14.76, 14.95, 15.08, 15.08, 15.15, 15.02, 15.08, 14.96, 14.94, 14.88, 14.63, 15.11, 14.9, 14.84, 14.49, 
    14.3, 14.24, 14.51, 14.38, 14.69, 14.71, 14.69, 14.63, 14.91, 15.1, 15, 15.16, 15.07, 14.86, 15.15, 15.03, 15.38, 15.45, 15.54, 15.63, 15.75, 15.84, 15.57, 15.47, 15.57, 15.57, 15.27, 15.36, 15.41, 15.65, 15.67, 15.32, 15.23, 14.83, 14.99, 14.87, 14.97, 15.26, 15.21, 15.37, 15.22, 15.25, 15.31, 15.23, 15.46, 15.56, 15.69, 15.67, 15.76, 15.69, 15.73, 15.34, 15.22, 15.39, 15.31, 15.22, 15.18, 15.32, 14.9, 14.76, 15.09, 15, 14.85, 14.33, 14.42, 14.34, 14.48, 14.42, 14.36, 14.34, 14.44, 14.51, 14.24, 
    14.17, 14.28, 14.27, 14.37, 14.43, 14.14, 14.08, 13.95, 13.7, 13.65, 13.46, 13.99, 13.94, 14.18, 13.87, 14.16, 14.48, 14.28, 14.19, 13.88, 13.94, 13.77, 13.99, 14.66, 14.55, 14.29, 14.74, 15.08, 15.29, 15.35, 15.29, 15.18, 15.19, 15.15, 15.29, 15.28, 15.11, 15.23, 15.2, 15.7, 15.62, 15.56, 15.42, 15.64, 15.76, 15.53, 15.37, 15.67, 15.6, 15.13, 15.25, 15.17, 15.18, 15.05, 15.02, 15.02, 15.4, 15.61, 15.11, 15.33, 14.76, 14.61, 14.63, 15.2, 15.01, 15.56, 15.73, 15.62, 15.57, 15.14, 15.42, 16.07, 
    15.88, 15.82, 16.42, 15.84, 15.25, 14.88, 15.15, 15.49, 14.85, 14.57, 14.57, 14.63, 14.47, 14.31, 14.04, 14.11, 13.59, 13.6, 13.59, 13.45, 13.42, 13.33, 12.98, 12.98, 12.71, 12.73, 12.67, 12.81, 12.55, 12.67, 12.79, 12.97, 12.96, 12.95, 12.88, 12.84, 12.92, 12.76, 12.85, 13.09, 12.99, 12.96, 13.16, 12.98, 13.4, 13.16, 13.19, 12.86, 12.76, 12.92, 12.58, 12.63, 12.36, 12.83, 12.79, 13.16, 13, 12.82, 13.06, 13.12, 13.41, 13.6, 13.11, 13.06, 12.59, 12.59, 12.57, 12.85, 12.71, 12.99, 13.25, 13.46, 
    13.28, 12.97, 13.07, 13.21, 13.63, 13.55, 13.23, 13.44, 12.94, 12.71, 13, 12.82, 12.57, 12.22, 12.52, 12.91, 12.52, 12.31, 12.45, 12.44, 12.55, 12.74, 12.55, 12.78, 12.49, 12.25, 13.6, 13.39, 13.41, 14.17, 14.47, 14.37, 14.39, 14.36, 14.17, 14.17, 14.09, 14.76, 14.12, 14.12, 13.85, 13.57, 13.49, 13.14, 13.16, 13.18, 12.93, 12.88, 12.63, 13.1, 13.1, 13.07, 13.39, 13.5, 13.35, 13.74, 13.41, 13.41, 13.31, 13.52, 13.72, 13.87, 13.97, 13.97, 14.37, 14.36, 14.39, 14.54, 14.56, 14.54, 14.75, 14.24, 
    14.26, 14.34, 14.39, 14.39, 14.46, 14.97, 14.58, 14.44, 14.15, 14.14, 14.22, 14.44, 14.32, 14.28, 13.78, 13.42, 13.61, 13.73, 13.12, 13.05, 13.22, 13.36, 13.1, 13.44, 13.06, 12.75, 13.29, 13.67, 13.9, 13.6, 13.56, 14.01, 14.23, 13.86, 14.53, 15.05, 15.12, 15.42, 15.29, 15.18, 15.32, 14.99, 14.77, 14.89, 15.13, 15.1, 15.14, 15.15, 15.14, 15.32, 15.07, 14.86, 14.71, 14.43, 14.32, 14.28, 14.29, 14.09, 14.13, 14.26, 14.3, 14.28, 14.54, 14.37, 13.66, 13.67, 13.56, 13.74, 14.08, 14.27, 14.39, 14.35, 
    14.44, 14.09, 14.02, 14.47, 14.45, 14.19, 14.61, 13.93, 13.73, 13.35, 13.1, 12.98, 12.96, 13.02, 13.13, 13.15, 13.41, 13.25, 13.32, 13.15, 12.85, 12.78, 13.15, 12.68, 12.73, 12.76, 12.19, 12.85, 13.22, 13.12, 12.99, 13.13, 13.89, 14.01, 14.1, 14.71, 14.93, 14.65, 14.92, 14.95, 14.74, 14.89, 14.89, 14.75, 14.96, 14.34, 14.09, 13.81, 14.16, 14.45, 14.87, 15.63, 15.23, 14.58, 14.27, 13.9, 14.51, 14.15, 13.92, 13.46, 13.17, 13.29, 13.5, 13.2, 13.32, 12.95, 12.87, 13.6, 13.67, 13.55, 13.9, 13.06, 
    13.06, 12.56, 12.12, 12.38, 12.18, 11.79, 11.9, 11.45, 10.89, 10.9, 10.62, 10.3, 10.96, 11.62, 10.96, 11.37, 11.97, 12.65, 12.28, 12.05, 11.6, 11.49, 11.78, 11.49, 10.65, 11.11, 11.47, 10.8, 9.95, 9.96, 10.43, 9.57, 9.19, 9.44, 9.76, 10.6, 9.52, 8.48, 8.27, 8.45, 8.06, 8.35, 9.17, 9.91, 9.87, 9.97, 10.18, 10.36, 11.01, 11.57, 11.61, 11.44, 11.63, 11.78, 11.4, 11.47, 11.22, 11.24, 11.34, 12.32, 12.93, 12.98, 13.45, 13.51, 14.01, 14.33, 15.02, 15.27, 14.93, 15.1, 15.45, 15.57, 15.36, 15.28, 15.28, 
    15.36, 15.67, 15.29, 15.26, 15.47, 15.47, 15.3, 14.88, 14.86, 14.37, 14.28, 14.45, 13.72, 14.82, 15.22, 15.36, 15.53, 15.52, 16.31, 15.63, 15.76, 15.86, 15.03, 14.92, 16.33, 16.55, 17.03, 17.43, 17.95, 17.95, 17.94, 18.51, 18.69, 18.2, 18.54, 18.94, 18.25, 17.94, 18.12, 18.45, 17.63, 17.87, 19.14, 20.19, 19.9, 21.25, 21.8, 21.68, 21.91, 22.82, 23.29, 22.84, 22.04, 22.5, 21.81, 22.25, 22.08, 23.07, 23.14, 22.83, 22.35, 23.19, 24.45, 24.67, 24.65, 25.06, 24.85, 24.68, 23.78, 23.25, 22.91, 23.03, 
    23.9, 23.07, 22.77, 22.86, 24.19, 24.4, 24.65, 24.45, 24.72, 24.96, 25.19, 25.17, 25.14, 24.72, 24.37, 24.58, 24.72, 24.42, 23.73, 23.59, 23.19, 23.43, 23.67, 23.31, 22.65, 22.61, 22.82, 22.26, 21.67, 21.21, 21.38, 22.06, 22.7, 23.63, 24.41, 24.94, 25.14, 24.74, 24.67, 24.49, 24.5, 25.76, 25.03, 26.32, 27.26, 27.45, 26.68, 26.02, 25.79, 27.51, 27.64, 27.45, 27.99, 29.33, 28.77, 28.34, 27.88, 27.59, 27.78, 27.77, 27.41, 27.64, 27.5, 27.24, 27.13, 27, 27.16, 27.32, 27.2, 27.49, 27.54, 26.44, 26.6, 
    27.13, 26.34, 26.1, 26.59, 26.19, 26.34, 26.38, 26.11, 26.06, 25.73, 25.36, 25.31, 24.89, 24.68, 24.46, 25.04, 25.39, 25.17, 24.91, 25.03, 25.31, 24.5, 23.56, 23.88, 24.19, 24.63, 24.74, 24.51, 25, 25.34, 25.23, 24.51, 24.69, 24.8, 25.14, 25, 24.38, 24.44, 23.69, 23.51, 23.82, 23.31, 23.47, 23.42, 22.52, 22.27, 21.76, 22.26, 22.51, 22.54, 21.97, 21.56, 21.66, 21.43, 22.21, 22.55, 21.95, 21.86, 21.66, 21.38, 21.35, 21.24, 20.67, 20.88, 21.31, 21.16, 21.26, 21.35, 21.59, 21.48, 21.7, 21.5, 21.64, 
    20.93, 20.87, 20.72, 19.93, 19.97, 20.16, 20.39, 20.44, 19.97, 18.84, 19.19, 19.22, 19.1, 20.08, 20.7, 20.65, 21.04, 19.76, 20.03, 20.31, 20.84, 22.28, 22.23, 22.75, 23.17, 23.41, 23.11, 23.11, 23.42, 23.7, 23.66, 23.55, 23.54, 22.92, 22.41, 22.21, 21.87, 22, 21.93, 22.3, 22.45, 0.01, 0.03, 0.03, 0.03, 0.03, 0.03, 0.03, 0.03, 0.03, 0.03, 0.03, 0.01, 0.04, 0.06, 0.07, 0.07, 0.08, 0.08, 0.07, 0.07, 0.08, 0.08, 0.09, 0.09, 0.1, 0.1, 0.1, 0.11, 0.1, 0.07, 0.07, 0.08, 0.08, 0.09, 0.07, 0.07, 0.07, 
    0.07, 0.07, 0.07, 0.07, 0.07, 0.07, 0.07, 0.07, 0.07, 0.07, 0.07, 0.07, 0.07, 0.07, 0.11, 0.07, 0.07, 0.08, 0.07, 0.08, 0.08, 0.08, 0.08, 0.08, 0.08, 0.08, 0.08, 0.06, 0.07, 0.07, 0.07, 0.09, 0.08, 0.09, 0.1, 0.1, 0.1, 0.1, 0.1, 0.1, 0.11, 0.1, 0.11, 0.11, 0.11, 0.11, 0.11, 0.11, 0.11, 0.11, 0.11, 0.11, 0.11, 0.1, 0.1, 0.1, 0.1, 0.09, 0.09, 0.09, 0.09, 0.11, 0.12, 0.11, 0.12, 0.12, 0.12, 0.12, 0.12, 0.13, 0.12, 0.13, 0.14, 0.13, 0.13, 0.13, 0.14, 0.14, 0.14, 0.15, 0.14, 0.13, 0.13, 0.14, 0.13, 
    0.14, 0.13, 0.13, 0.11, 0.12, 0.12, 0.13, 0.14, 0.14, 0.17, 0.19, 0.22, 0.24, 0.25, 0.27, 0.27, 0.29, 0.28, 0.29, 0.29, 0.29, 0.27, 0.27, 0.3, 0.29, 0.29, 0.29, 0.29, 0.3, 0.28, 0.3, 0.33, 0.29, 0.33, 0.32, 0.3, 0.4, 0.47, 0.53, 0.54, 0.54, 0.56, 0.58, 0.53, 0.53, 0.54, 0.64, 0.68, 0.68, 0.63, 0.51, 0.56, 0.68, 0.72, 0.76, 0.8, 0.8, 0.83, 0.83, 0.83, 0.85, 0.9, 1.03, 1.31, 1.36, 1.2, 1.04, 1, 1, 1, 1.05, 1.05, 1.05, 1.2, 1.25, 1.25, 1.25, 1.35, 1.35, 1.15, 1.15, 1.05, 1, 1.1, 1, 0.95, 1, 1, 0.95, 
    0.9, 0.95, 0.9, 0.8, 1.15, 1.15, 1.2, 1.25, 1.3, 1.65, 1.5, 1.35, 1.5, 1.8, 2, 2.25, 2.35, 2.45, 2.5, 3.05, 3.3, 3.45, 3.8, 3.9, 4, 4, 4.1, 4.25, 4.05, 4.05, 4, 3.85, 3.5, 3.95, 4.8, 4.85, 4.85, 5.6, 6.6, 6.7, 6.7, 6.95, 6.95, 6.8, 6.6, 6.65, 6.7, 6.6, 6.6, 6.6, 6.85, 7.1, 7.3, 7.55, 7.1, 6.85, 7.25, 7.65, 8.2, 8.4, 8.9, 9.2, 9.2, 9, 8.9, 9.1, 9, 8.75, 8.9, 9.25, 9.4, 8.7, 8.95, 9.7, 9.7, 9.65, 10.55, 10.8, 10.95, 11.25, 11.25, 11.05, 12.15, 12.4, 12.35, 12.8, 12.75, 13.05, 13.05, 13.15, 13, 
    12.8, 12.75, 12.65, 12.75, 12.75, 12.65, 12.4, 12.45, 12.3, 12.3, 12.5, 13.3, 12.9, 12.45, 12.35, 13.25, 13.85, 14, 14.7, 16.25, 16.75, 16.75, 16.8, 16.8, 16.9, 16.8, 16.95, 17.05, 17.15, 17.1, 16.9, 16.5, 16.5, 16.3, 16.6, 16.9, 17, 16.9, 17.4, 17.6, 17.35, 16.55, 16.45, 16.4, 16.25, 16.25, 16.5, 16.3, 16.5, 16.55, 16.45, 15.9, 16.6, 17.15, 17.05, 16.85, 16.9, 17.35, 17.15, 17, 17.3, 17.4, 17.55, 17.2, 17.7, 18.05, 17.5, 17.15, 17.05, 17.1, 16.95, 16.8, 17.05, 16.65, 16.85, 16.85, 16.55, 16.55, 
    16.2, 15.75, 15.6, 16.05, 16.15, 16.05, 16.6, 15.9, 15.65, 15.5, 15.5, 15.5, 15.6, 14.6, 14.6, 15.6, 16.3, 16.65, 17.05, 17, 17.4, 18.5, 19.55, 19.85, 19.75, 20.45, 18.95, 16.95, 16.25, 16.25, 17.35, 15.75, 9.8, 13.4, 13.65, 12.75, 12.65, 13.2, 14.85, 12.85, 11.95, 13.95, 14.25, 17.3, 20.75, 28.3, 30.95, 30.75, 30.95, 31.5, 31.5, 30.3, 30.15, 30.35, 30.45, 30, 29.85, 30.35, 29.8, 28.85, 28.35, 28.4, 28.35, 28.2, 27.95, 27.8, 27.95, 28.2, 28.15, 28.1, 28.15, 27.95, 27.7, 28.05, 28.25, 28.45, 27.9, 
    27.7, 27.75, 27.6, 28.05, 28.05, 28.15, 27.85, 27.4, 27.2, 27.65, 27.65, 28.2, 28.3, 28.1, 27.7, 27.95, 27.6, 27.35, 27.2, 27.3, 27.45, 27.15, 27.65, 28.7, 28.85, 28.55, 28.05, 27.55, 27.5, 26.9, 27.45, 26.7, 26.35, 26.9, 27.9, 26.65, 26.45, 25.25, 24.05, 24, 24, 23.8, 23.8, 23.7, 24, 23.45, 23.05, 22.75, 22.1, 22.05, 21.85, 21.65, 21.35, 21.65, 21.85, 21.95, 22.1, 22.1, 22.4, 22.45, 22.7, 22.35, 21.7, 22.05, 22.9, 23.4, 22.7, 21.8, 20.55, 20.15, 19.9, 20.5, 20.15, 19.9, 21.6, 22.2, 21.7, 21.65, 
    22.45, 22.75, 22.9, 23.15, 22.7, 22.7, 22.5, 22.05, 21.6, 21.35, 21.25, 21.35, 21.75, 21.9, 22.1, 21.85, 21.65, 21.4, 21.45, 21.8, 22.1, 22.4, 22.85, 23.1, 23.05, 23.45, 23.5, 23.15, 23.05, 23.05, 23.6, 23.8, 23.3, 22.75, 22.85, 22.9, 22.75, 22.05, 21.6, 22.05, 22.3, 22, 22.05, 22.6, 22.05, 22.7, 22.45, 21.75, 22.25, 23.75, 24.35, 24.7, 24.65, 24.75, 24.75, 24.4, 23.95, 23.65, 23.55, 23.35, 23.1, 23.1, 23.05, 22.9, 22.75, 22.8, 22.45, 22.4, 22.8, 22.55, 22.45, 22.45, 21.75, 21.25, 20.5, 20.7, 
    20.7, 21.45, 22.35, 22.05, 22.05, 20.8, 20.15, 20.1, 20.35, 20.9, 24.55, 24.7, 24.3, 24, 27.95, 29.45, 29.9, 29.7, 29.4, 29.3, 28.85, 29.45, 26.9, 25.8, 25.45, 24.5, 23.95, 24, 23.4, 23.2, 23, 22.95, 21.5, 20.6, 20.1, 19.9, 19.85, 19.65, 19.65, 19.8, 19.6, 19.3, 19.1, 19.5, 19.6, 19.9, 19.65, 19.75, 19.95, 19.1, 18.5, 18.75, 18, 17.45, 17.2, 16.9, 16.8, 16.75, 16.9, 17.1, 17, 16.6, 16.6, 16.2, 16.25, 16.5, 16, 16.45, 17.2, 17.55)) %>% mutate(period = as.Date(period,origin="1970-01-01"))

target <- co2price %>%
  slice(1,3,6,7)

emi <- data.frame(period=c(2020, 2025, 2030, 2035, 2040, 2045, 2050, 2055, 2060), value = c(3468.15352891683, 2972.06819361702, 2143.69869003868, 1410.85633665377, 774.767006576402, 307.68052959381, -17.0576368471954, -76.1522979690523, -113.464199903288)) %>% mutate(period = as.Date(paste0("01/01/", period),format="%m/%d/%Y"))

targetEmi <- emi %>%
  slice(1,3,7)

histEmi <- data.frame(period=c(2005, 2006, 2007, 2008, 2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019, 2020, 2021, 2022), value = c(4446.18912078, 4460.81737191, 4472.39720286, 4335.32157486, 3992.70354621, 4072.80607426, 3971.86210198, 3894.24474603, 3788.72756238, 3660.91875424, 3720.64891711, 3733.94502803, 3837.39906824, 3760.17132584, 3612.57122998, 3229.09637181, 3417.14444046, 3378.70939976)) %>% mutate(period = as.Date(paste0("01/01/", period),format="%m/%d/%Y"))

data <- rbind(
  co2price %>% mutate(variable = "co2Price", type = "EU-27 Carbon price (/t CO2)"),
  ETSprice %>% mutate(variable = "ETSprice", type = "EU-27 Carbon price (/t CO2)"),
  target   %>%  mutate(variable = "target", type = "EU-27 Carbon price (/t CO2)"),
  emi      %>%  mutate(variable = "emi", type = "EU-27 GHG emissions (Mt CO2 eq/yr)"),
  targetEmi%>%  mutate(variable = "target", type = "EU-27 GHG emissions (Mt CO2 eq/yr)"),
  histEmi  %>%  mutate(variable = "histEmi", type = "EU-27 GHG emissions (Mt CO2 eq/yr)")
)


```

```{r create_plot, echo=FALSE, include=FALSE}

library(ggplot2)
library(ggrepel)

label <- data %>% filter(variable == "target") %>%
  mutate(label=c("A","B","C","D","A","B","D"))

plot <- ggplot(data,aes(x=period,y=value)) +
  geom_point(data=data %>% filter(variable == "target", period != as.Date("01/01/2045",format="%m/%d/%Y")), size = 3) +
  geom_point(data=data %>% filter(variable == "target", period == as.Date("01/01/2045",format="%m/%d/%Y")), size = 3, color = "#bbbbbb") +
  geom_line(data=data %>% filter(variable == "co2Price"), linewidth = 1) + 
  geom_line(data=data %>% filter(variable == "ETSprice"),linewidth=0.5, color = "#bbbbbb") +
  geom_line(data=data %>% filter(variable == "emi"), linewidth = 1) +
  geom_line(data=data %>% filter(variable == "histEmi"),linewidth=0.5, color = "#bbbbbb") +
  geom_label_repel(data=label, aes(x=period, y=value, label = label),
                   #nudge_x = c(-200,-200,200,200),
                   nudge_y = c(75,75,-75,-75,-750,-750,750)
                   ) +
  facet_wrap( vars(type) , ncol = 1, scales= "free_y") +
  scale_x_date(date_labels = "%Y") +
  theme_minimal() +
  theme(axis.title.y = element_blank(),
        axis.title.x=element_blank())


```


```{r, echo=FALSE, fig.width=6.5, fig.height=4}

plot

```


</div>
</div>

<div class = "row">

---

### Examples  

| **Example**                            | **cm_emiMktTarget**                                                    | **Description**                                                                                       |
|----------------------------------------|------------------------------------------------------------------------|-------------------------------------------------------------------------------------------------------|
| Single Regional Target                 | `2020.2050.EU27.all.year.netGHG_LULUCFGrassi 0.0001`                      | EU27 economy-wide (`all`) 2050 net-neutrality (`2050`, `year`) of GHG with bunkers emissions and LULUCF Grassi shift (`netGHG_LULUCFGrassi`)       |
| Multi-period Target                    | `2020.2030.EU27_regi.all.year.netGHG_LULUCFGrassi_intraRegBunker 2.191` , `2020.2050.EU27.all.year.netGHG 0.0001`| EU27 economy-wide (`all`) GHG emission target including only intra-region bunkers (`netGHG_LULUCFGrassi_intraRegBunker`) for 2030, and including full bunkers (`netGHG`) for 2050                          |
| Multi-period, Multi-regional Target    | `2020.2030.EU27_regi.all.year.netGHG_LULUCFGrassi_intraRegBunker 2.191`, `2020.2030.DEU.all.year.netGHG_noLULUCF_noBunkers 0.42`, `(2035.2050.EU27_regi, 2035.2045.DEU, 2020.2050.UKI).all.year.netGHG_LULUCFGrassi 0.0001` | 2030, 2045 and 2050 emission targets for Germany, EU27, and UK regions                    |
||||



</div>

</div>

<div class = "divisor">
</div>

<div class = "column33">

### Emission Target Definition  

`cm_emiMktTarget` follows this format:  

`initial_year`.`target_year`.`region`.`group_of_sectors`.`type_of_target`.`emissions_type` `value`

### Configuration Parameters  

| **Parameter**        | **Set**              | **Values**                             | **Description**                                                                                   |
|----------------------|----------------------|----------------------------------------|---------------------------------------------------------------------------------------------------|
| `initial_year`       | `ttot`               | year with four digits                  | Year when price increase starts and budget calculation begins                                     |
| `target_year`        | `ttot`               | year with four digits                  | Year when the emission target or budget is achieved                                               |
| `region`             | `ext_reg`            | ISO3 code or REMIND region code        | Region where the target applies                                                                   |
| `group_of_sectors`   | `emiMktExt`          | `all`, `ETS`, `ESR`, `other`           | Targeted emission markets: all emissions, ETS market, Effort Sharing market, or other markets     |
| `type_of_target`     | `target_type_47`     | `budget`, `year`                       | Emission target type: a cumulative budget or specific year-based reduction                        |
| `emissions_type`     | `emi_type_47`        | Various options (see below)            | Specifies CO2 or GHG target type (net or gross, with/without LULUCF or bunker emissions)          |
| `value`              |                      | Gt CO2e                                | Emission target value                                                                             |
|                      |                      |                                        |                                                                                                   |


### Emission Type Options  
- **CO2 Emission Targets:**  
  - `netCO2`, `netCO2_noBunkers`, `netCO2_noLULUCF_noBunkers`,  
    `netCO2_LULUCFGrassi`, `netCO2_LULUCFGrassi_noBunkers`, `netCO2_LULUCFGrassi_intraRegBunker`  
  - `grossEnCO2_noBunkers`  

- **GHG Emission Targets:**  
  - `netGHG`, `netGHG_noBunkers`, `netGHG_noLULUCF_noBunkers`,  
    `netGHG_LULUCFGrassi`, `netGHG_LULUCFGrassi_noBunkers`, `netGHG_LULUCFGrassi_intraRegBunker`,  
    `netGHG_noLULUCF`  

---

</div>
</div>
